---
title: "Foodweb comparisons"
author: "Emil De Borger"
date: '2022-10-06'
editor_options: 
  markdown: 
    wrap: 80
output:
  pdf_document:
    toc: yes
    extra_dependencies: ["float"]
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(fig.pos = "H", out.extra = "")

# Packages 
require(LIM)
require(tidyr)
require(dplyr)
require(NetIndices)
require(magrittr)
require(ggplot2)
require(ggh4x)
require(ggpmisc)
require(ggrepel)
require(factoextra)
require(vegan)
source("~/GitHub/Foodweb_publication/auxfuns.R")

library(devtools)
install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")
require(pairwiseAdonis)

```

# Load data

-   Loading model output from separate foodwebs from other scripts.

```{r load data, echo = FALSE}

# Lims
load(file = "./finalresults/limcoarse.rda") # LIM.coarse
load(file = "./finalresults/limfine.rda")   # LIM.fine
load(file = "./finalresults/limowf.rda")    # LIM.owf

# Solutions
load(file = "./finalresults/solldeicoarse.rda") # Solldeicoarse
load(file = "./finalresults/solldeifine.rda")   # Solldeifine
load(file = "./finalresults/solldeiowf.rda")    # Solldeiowf

# Flows
load(file = "./finalresults/Flows_coarse_iso.Rdata") # Flows.Coarse
load(file = "./finalresults/Flows_fine_iso.Rdata")   # Flows.Fine
load(file = "./finalresults/Flows_owf_iso.Rdata")    # Flows.owf

# Results tables
load("./finalresults/restab_coarse_iso.Rdata") # restabcoarse
load("./finalresults/restab_fine_iso.Rdata")   # restabfine
load("./finalresults/restab_owf_iso.Rdata")    # restabowf

# Fish
load("./finalresults/fish_coarse_iso.Rdata") # fishcoarse
load("./finalresults/fish_fine_iso.Rdata")   # fishfine
load("./finalresults/fish_owf_iso.Rdata")    # fishowf

# Foodweb indices
load("./finalresults/coarseindtable.rda") # NICOARSE
load("./finalresults/fineindtable.rda")   # NIfine
load("./finalresults/owfindtable.rda")    # NIowf_2

load("./finalresults/NETINDCOARSE.rda") #, netindcoarse
load("./finalresults/NETINDfine.rda")   #, netindfine
load("./finalresults/NETINDowf.rda")    #, netindowf

```

# Key to the species

Species names/group names were coded to ease writing the foodweb code. Here are
these codes and what they mean.

```{r , echo = F}

nmscoarse <- read.table("./BPNS_input_files/nmscoarse.txt", sep = ";")
nmsfine   <- read.table("./BPNS_input_files/nmsfine.txt", sep = ";")
nmsowf    <- read.table("./BPNS_input_files/nmsowf.txt", sep = ";")

keycoarse <- cbind("Code" = LIM.coarse$Components[,1], "Names" = nmscoarse[1:41, 1], "Biomass (mmol C m-2)" = LIM.coarse$Components[, 2])
keyfine   <- cbind("Code" = LIM.fine$Components[,1]  , "Names" = nmsfine[1:46, 1]  , "Biomass (mmol C m-2)" = LIM.fine$Components[, 2])
keyowf    <- cbind("Code" = LIM.owf$Components[,1]   , "Names" = nmsowf[1:65, 1]   , "Biomass (mmol C m-2)" = LIM.owf$Components[, 2])

knitr::kable(keycoarse, caption = "Key to Coarse foodweb codes")
knitr::kable(keyfine  , caption = "Key to Fine foodweb codes")
knitr::kable(keyowf   , caption = "Key to OWF foodweb codes")

write.table(keycoarse, "./paper_figures_tables/tables/key_coarse.txt", quote = FALSE)
write.table(keyfine  , "./paper_figures_tables/tables/key_fine.txt"  , quote = FALSE)
write.table(keyowf   , "./paper_figures_tables/tables/key_owf.txt"   , quote = FALSE)

```

# Foodweb plots

Notes

-   These figures are NOT used in the final manuscript.
-   Circles next to species denote cannibalism.
-   Simplified plots are without DIC and export fluxes to decrease the number of
    arrows.

## Coarse

-   *E. cordatum*, suspension feeding bivalves and crabs are important inputs of
    water column material into the sediment.

```{r 330 foodweb, fig.height = 16, fig.width = 16, echo = FALSE, message = FALSE, fig.cap = "330 foodweb"}

matcoarse  <- Flowmatrix(lim = LIM.coarse, web = Solldeicoarse$X+1)
matcoarseb <- matcoarse[-c(41:44), -c(41:44)]

# full
plotweb(Flowmatrix(lim = LIM.coarse, web = Solldeicoarse$X+1), main="Coarse Foodweb", 
        bty="n", lab.size= 1.2, names = nmscoarse[,1], log = T, leg.title = "log + 1")

# simplified
plotweb(matcoarseb, main="Coarse Foodweb - Simplified", 
        bty="n", lab.size=1.2, names = nmscoarse[1:40,1], log = T, leg.title = "log + 1")

```

## Fine

-   Bivalves and suspension feeding polychaetes are main inputs of water column
    material the sediment foodweb.

```{r 780 foodweb, fig.height = 16, fig.width = 16, echo = FALSE, message = FALSE, fig.cap = "780 foodweb"}

matfine <- Flowmatrix(lim = LIM.fine, web = Solldeifine$X+1)
matfineb <- matfine[-c(47:49), -c(47:49)]

# full
plotweb(Flowmatrix(lim = LIM.fine, web = Solldeifine$X+1), main="Fine Foodweb", 
        bty="n", lab.size=1.2, names = nmsfine[,1], log = T, leg.title = "log + 1")

# simplified
plotweb(matfineb, main="Fine Foodweb - Simplified", 
        bty="n", lab.size=1.2, names = nmsfine[c(1:46),1], log = T, leg.title = "log + 1")

```

## OWF

-   Suspension feeding bivalves (*M. edulis*) are the main input of OM into the
    foodweb.

```{r D6 foodweb, fig.height = 16, fig.width = 16, echo = FALSE, message = FALSE, fig.cap = "D6 foodweb"}

matowf <- Flowmatrix(lim = LIM.owf, web = Solldeiowf$X+1)
matowfb <- matowf[-c(66:68), -c(66:68)]

# full
plotweb(Flowmatrix(lim = LIM.owf, web = Solldeiowf$X+1), main="OWF Foodweb", 
        bty="n", lab.size=1.2, names = nmsowf[,1], log = T, leg.title = "log + 1")

# simplified
plotweb(matowfb, main="OWF Foodweb - Simplified", 
        bty="n", lab.size=1.2, names = nmsowf[1:65, 1], log = T, leg.title = "log + 1")

```

# Foodweb component comparisons

## Macrofauna
- Weight percentage of total biomass each macrofaunal group

```{r label, options}
 # relative weight % of macrofauna of total biomass
maccoarse <- data.frame("Name" = LIM.coarse$Parameters$name[12:35], "Weight" = as.numeric(LIM.coarse$Parameters$val[12:35]))
maccoarse$rel <- round(maccoarse$Weight/sum(maccoarse$Weight)*100,2)

macfine <- data.frame("Name" = LIM.fine$Parameters$name[12:40], "Weight" = as.numeric(LIM.fine$Parameters$val[12:40]))
macfine$rel <- round(macfine$Weight/sum(macfine$Weight)*100,2)

macowf <- data.frame("Name" = LIM.owf$Parameters$name[15:59], "Weight" = as.numeric(LIM.owf$Parameters$val[15:59]))
macowf$rel <- round(macowf$Weight/sum(macowf$Weight)*100,2)

# Subdivision for OWF food web
macowftur <- data.frame("Name" = LIM.owf$Parameters$name[15:36], "Weight" = as.numeric(LIM.owf$Parameters$val[15:36]))
macowftur$rel <- round(macowftur$Weight/sum(macowftur$Weight)*100,2)

macowfsof <- data.frame("Name" = LIM.owf$Parameters$name[37:54], "Weight" = as.numeric(LIM.owf$Parameters$val[37:54]))
macowfsof$rel <- round(macowfsof$Weight/sum(macowfsof$Weight)*100,2)

macowfubi <- data.frame("Name" = LIM.owf$Parameters$name[55:59], "Weight" = as.numeric(LIM.owf$Parameters$val[55:59]))
macowfubi$rel <- round(macowfubi$Weight/sum(macowfubi$Weight)*100,2)

```

## Fish
- Weight percentage of total biomass each fish group

```{r label, options}

fishcoarse <- data.frame("Name" = LIM.coarse$Parameters$name[1:10], "Weight" = as.numeric(LIM.coarse$Parameters$val[1:10]))
fishcoarse$rel <- round(fishcoarse$Weight/sum(fishcoarse$Weight)*100,2)

fishfine <- data.frame("Name" = LIM.fine$Parameters$name[1:10], "Weight" = as.numeric(LIM.fine$Parameters$val[1:10]))
fishfine$rel <- round(fishfine$Weight/sum(fishfine$Weight)*100,2)

fishowf <- data.frame("Name" = LIM.owf$Parameters$name[1:13], "Weight" = as.numeric(LIM.owf$Parameters$val[1:13]))
fishowf$rel <- round(fishowf$Weight/sum(fishowf$Weight)*100,2)

```

## Ordination to show differences in composition

- Ordination plot used in the manuscript - postprocessing done in Adobe Illustrator

```{r}
require(vegan)

dat <- read.table("ordinationinput.csv", header = TRUE, sep = ";")

datprep <- t(dat[,c(2:4)])
colnames(datprep) <- dat[,1]

## MDS
mdsout <- metaMDS(t(datprep))
ordiplot(mdsout, type = "t")

##--> Points en species (sites) plotten
spdat <- data.frame(mdsout$points)
spdat$name <- row.names(spdat)
spdat$location <- dat$Loc

fwdat <- data.frame(mdsout$species)
fwdat$name <- row.names(fwdat)

spdat$MDS2 <- -spdat$MDS2
fwdat$MDS2 <- -fwdat$MDS2

# geom_text_repel(aes(label = stringr::str_wrap(descs, 20))) +

spdat$location <- as.factor(spdat$location)
cpal <- c("#F0E442", "#0072B2", "#009E73", "#D55E00", "#E69F00", "#806647", "black")

ggplot(spdat, aes(x = MDS1, y = MDS2, color = location)) +
  scale_shape_manual(values=1:9) +
          geom_point(size = 2) +
          geom_text_repel(aes(label = stringr::str_wrap(name, 15)), size = 3, force = 1.5, direction = c("both"), max.overlaps = 40, max.time = 60, force_pull = 0.001) + 
           scale_color_manual(values = cpal) + 
           xlim(-1.5, 1.1) + 
           geom_text_repel(data = fwdat, aes(x = MDS1, y = MDS2, label = name), size = 4, col = "black") +
           geom_point(data = fwdat, aes(x = MDS1, y = MDS2, shape = name), size = 3, col = "black") +
           theme_bw() + 
           labs(x = "MDS 1", y = "MDS 2", color = "Occurs in", shape = "Food web") + 
           theme(axis.title.x = element_text(size=14),
                 axis.title.y = element_text(size=14),
                 strip.text.x = element_text(size = 14))

ggsave("./paper_figures_tables/figures/mds2.png", width = 10, height = 7, units = "in", dpi = 300)

```

# Overviews

- Overview of some base qualities of the three foodwebs, NOT used in the manuscript.

```{r}

what <- rep(c("Animal biomass", "Macrofauna biomass", "Fish biomass", "Number of species", "Total System Throughput (TST)", "components", "unknowns"), 3)
what <- factor(what, levels = c("Animal biomass", "Macrofauna biomass", "Fish biomass", "Number of species", "Total System Throughput (TST)", "components", "unknowns"))

vals <- c(2047.2 , 2042.9 , 4.3 , 57 , 762.6, 41, 453,
          12894.2, 12881.8, 12.4, 92 , 948.7, 46, 536,
          662.0  , 657.1  , 4.9 , 120, 763.9, 65, 853)

fw <- rep(c("Coarse", "Fine", "OWF"), each = 7)

overviewdf <- data.frame("var" = what, "foodweb" = fw, "val" = as.numeric(vals))
overviewdfsub <- overviewdf[overviewdf$var %in% c("Macrofauna biomass", "Fish biomass", "Number of species", "Total System Throughput (TST)"),]

overviewfig <- ggplot(data = overviewdfsub, aes(x = foodweb, y = val, fill = foodweb)) + 
               geom_bar(stat = "identity", position = position_dodge()) + 
               scale_fill_viridis_d(option = "viridis") + 
               geom_text(aes(label = val), hjust = - 0.2, color = "black", position = position_dodge(0.9), size = 4, angle = 90) + 
               facet_wrap(~var, ncol = 4, scales = "free_y",
                          labeller = as_labeller(
                            c(`Macrofauna biomass` = "Macrofauna biomass (mmol m-2)",
                              `Fish biomass` = "Fish biomass (mmol m-2)",
                              `Number of species` = "Number of species (n)",
                              `Total System Throughput (TST)` = "Total System Throughput (mmol C m-2 d-1)")),
                          strip.position = "left") + 

  scale_y_continuous(expand = c(0.3, 0.0)) +  coord_cartesian(ylim = c(0, NA), clip = "off") +
               labs(fill = "Food web") + 
               xlab(" ") +
               ylab(" ") + 
               theme_classic() + 
               theme(strip.background = element_blank(), strip.placement = "outside",
                     axis.text.y = element_text(size = 12),
                     axis.text.x = element_text(size = 12))

overviewfig

ggsave("./paper_figures_tables/figures/basicstats_presentation.png", height = 5, width = 12)


```

# Barplot output

- The supporting data of these graphs is given in tabular form below the barplots.
- Figures not shown in the final manuscript

## Totals

-   OMdeposition : SPOM -\> SOM flux
-   Total respiration : All DIC producing fluxes, incl. bacteria and plankton
-   Burial : Burial flux constrained by FaCE-It mass budget modelling
-   Total export : All export fluxes
-   Total carbon outflow : DIC + Export + Burial fluxes
-   Total carbon inflow : Primary productivity
    
```{r barplot totals, fig.height = 10, fig.width = 15, echo = FALSE, warning = FALSE, message = FALSE}

nms    <- c("name", "Coarse", "Fine", "OWF")
dfmean <- cbind(restabcoarse[c(1, 8, 9, 10, 26, 27), c(1, 2)], 
                restabfine[c(1, 8, 9, 10, 26, 27), 2],
                restabowf[ c(1, 8, 9, 10, 26, 27), 2])
dfsd   <- cbind(restabcoarse[c(1, 8, 9, 10, 26, 27), c(1, 3)], 
                restabfine[c(1, 8, 9, 10, 26, 27), 3],
                restabowf[ c(1, 8, 9, 10, 26, 27), 3])
colnames(dfmean) <- nms
colnames(dfsd)   <- nms

y      <- as.matrix(t(round(dfmean[, 2:4], 2)))
par(mfrow = c(1,1))
a <- barplot(t(dfmean[, (2:4)]), beside = T, main = "Totals", names.arg = dfmean[,1],
             ylab = "mmol C m-2", cex.names = 0.8, space = rep(c(0.8, 0.2, 0.2), 6),
             ylim = c(0, 270)) # , space = 0.01) #, xlim = c(0, 3.5))
arrows(a, t(dfmean[, 2:4] + dfsd[, 2:4]), a, t(dfmean[, 2:4] - dfsd[, 2:4]), 
       length = 0.05, code = 3, angle = 90, lwd = 1)
legend("topleft", c("Coarse", "Fine", "OWF"), bty = "n", fill = gray.colors(3))
text(a, y + 4, labels = as.character(y), cex = 0.8)

```

## Respiration

-   Summed respiration of different components.
-   Water respiration includes plankton respiration.

Remarks:

```{r barplot respiration table, fig.height = 10, fig.width = 15, echo = FALSE, warning = FALSE, message = FALSE}

dfmean <- cbind(restabcoarse[c(2:8), c(1,2)], 
                restabfine[c(2:8), 2],
                restabowf[ c(2:8), 2])
dfsd   <- cbind(restabcoarse[c(2:8), c(1,3)], 
                restabfine[c(2:8), 3],
                restabowf[ c(2:8), 3])
colnames(dfmean) <- nms
colnames(dfsd)   <- nms 


y      <- as.matrix(t(round(dfmean[, 2:4], 2)))

par(mfrow = c(1,1))
a <- barplot(t(dfmean[, (2:4)]), beside = T, main = "Respiration", names.arg = dfmean[,1],
             ylab = "mmol C m-2", cex.names = 0.8, space = rep(c(0.8, 0.2, 0.2), 7), ylim = c(0, 110))

arrows(a, t(dfmean[, 2:4] + dfsd[, 2:4]), a, t(dfmean[, 2:4] - dfsd[, 2:4]), 
       length = 0.05, code = 3, angle = 90, lwd = 1)

legend("topleft", c("Coarse", "Fine", "OWF"), bty = "n", fill = gray.colors(3))

text(a, y + 4, labels = as.character(y), cex = 0.8)

```

## Uptake macrofauna by groups

-   Uptake of phytoplankton, zooplankton, SOM, and SPOM foodsources by
    macrofauna (all)
-   Total uptake by macrofauna
-   Uptake of detrital forms by bacteria

```{r barplot water column, fig.height = 10, fig.width = 15, echo = FALSE, warning = FALSE, message = FALSE}

dfmean <- cbind(restabcoarse[c(11:17), c(1,2)], 
                restabfine[c(11:17), 2],
                restabowf[ c(11:17), 2])
dfsd   <- cbind(restabcoarse[c(11:17), c(1,3)], 
                restabfine[c(11:17), 3],
                restabowf[ c(11:17), 3])
colnames(dfmean) <- nms
colnames(dfsd)   <- nms

nms2 <- c("phytopl.->macrofauna", "zoopl.->macrofauna", "SOM->macrofauna", "SPOM->macrofauna", "Total->macrofauna", "SOM->bacteria", "SPOM->bacteria")

```

### Figure 3

- Barplot macrofauna uptake
- Postprocessing performed with Adobe illustrator

```{r}

coarsedflim <- coarsedf[coarsedf$bg == "All",]
finedflim   <- finedf[finedf$bg == "All",]
owfdflim    <- owfdf[owfdf$bg == "All", -4]

owfdflimsum <- owfdflim %>%
  group_by(fs) %>%
  summarize(
    owf = first(owf),
    bg = first(bg),
    name = paste(name, collapse = ", "),
    mean = sum(mean, na.rm = TRUE),
    owfdfsd = sum(owfdfsd, na.rm = TRUE)
  )


names(finedflim) <- colnames(coarsedflim)
owfdflimsum <- owfdflimsum[,c(2,1,3,4,5,6)]
names(owfdflimsum) <- colnames(coarsedflim)

alldfs <- rbind(coarsedflim, finedflim, owfdflimsum)
alldfs$mean <- round(alldfs$mean, 1)

alldfuptake <- ggplot(data = alldfs, aes(x = crse, y = mean, fill = fs)) +
                     geom_bar(stat = "identity", position = position_dodge(0.9)) + 
                     geom_text(aes(label = round(mean,2)), hjust = - 0.75, color = "black", position = position_dodge(0.9), size = 4.5, angle = 90) + 
                     geom_errorbar(aes(ymin = mean - coarsedfsd, ymax = mean + coarsedfsd), width=.2,
                                   position = position_dodge(.9)) + 
                     ylim(0, 90) +
  scale_y_continuous(expand = expansion(mult = 0)) + 
                     labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Foodsource", title = "") +
                     scale_fill_viridis_d(option = "viridis") + 
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                           legend.text = element_text(size = 12))


owfdfshort <- owfdf[owfdf$bg == "All",]
  
owfuptakepres <- ggplot(data = owfdfshort, aes(x = comm, y = mean, fill = fs)) +
                    geom_bar(stat = "identity", position = position_dodge()) + 
                    geom_text(aes(label = round(mean,1)), hjust = - 0.5, color = "black", position = position_dodge(0.9), size = 4.5, angle = 90) + 
                    geom_errorbar(aes(ymin=mean-owfdfsd, ymax=mean+owfdfsd), width=.2,
                                 position=position_dodge(.9)) + 
                    labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Foodsource", title = " ") +
                    scale_fill_viridis_d(option = "viridis") + 
  scale_y_continuous(expand = expansion(mult = 0)) + 
                      ylim(0, 15) + 
                     theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                          legend.text = element_text(size = 12))
owfuptakepres

library(patchwork)
layout <- "1
           2"

uptake3 <- alldfuptake + owfuptakepres

uptake3 <- uptake3 + plot_layout(design = layout, guides = "collect") + plot_annotation(tag_levels = 'A') & theme(legend.position = 'right')

uptake3
ggsave("./paper_figures_tables/figures/figure3.png", height = 8, width = 8)

```

### Figure 4: Fish uptake

- Postprocessing performed with adobe illustrator

#### Coarse

```{r}

`%notin%` <- Negate('%in%')

fishnicecoarse <- rep(c("Callionymiformes",
                        "Carangiformes",
                        "Gadiformes",
                        "Gobiiformes",
                        "Mulliformes",
                        "Cottoidei",
                        "Percoidei",
                        "Scorpaenidei",
                        "Ammodytidae",
                        "Pleuronectiformes"), each = 10)

Fishcoarse$fishnice <- fishnicecoarse

Fishcoarse <- Fishcoarse[Fishcoarse$name %notin% c("Benthos", "Phyto"),]

fishcoarse_levels <- rep(names(sort(tapply(Fishcoarse$mean, Fishcoarse$fishnice, sum), decreasing = TRUE)), each = 8)
Fishcoarse$fishnice <- factor(Fishcoarse$fishnice, levels = rev(unique(fishcoarse_levels)))

Fishcoarse$prey   <- factor(Fishcoarse$name, levels = c("Zoo", "SPOM", "SOM", "Biv", "Crust", "Poly", "Other", "Pisc"), labels = c("Zooplankton", "SPOM", "SOM", "Bivalves","Crustaceans","Polychaetes","Others", "Fish"))

### Subset of shared fishspecies

sharedspecies <- c("Pleuronectiformes",
                   "Callionymiformes",
                   "Gadiformes",    
                   "Cottoidei",
                   "Carangiformes",                 
                   "Scorpaenidei",
                   "Gobiiformes",                        
                   "Percoidei")

Fishcoarsesub <- Fishcoarse[Fishcoarse$fishnice %in% sharedspecies,]
Fishcoarsesub$fishnice <- factor(Fishcoarsesub$fishnice, levels = rev(sharedspecies))

fishcoarsesubplot <- ggplot(data = Fishcoarsesub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity") + 
                 coord_flip() + 
                 scale_fill_viridis_d(option = "viridis") + 
                 scale_y_continuous(expand = expansion(mult = 0), limits = c(0, 0.5)) +
                 labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Food source", title = "Coarse") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                           legend.text = element_text(size = 12))

fishcoarsesubplot

## Proportional subset
fishcoarseprop2 <- ggplot(data = Fishcoarsesub, aes(x = fishnice, y = mean, fill = prey)) +
                  geom_bar(stat = "identity", position = "fill") + 
                  coord_flip() + 
                  scale_fill_viridis_d(option = "viridis") + 
                   scale_y_continuous(expand = expansion(mult = 0)) +
                  labs(x = " ", y = expression(paste("proportion of uptake")), fill = "Food source", title = "Coarse") +
                  
                  theme_classic()
fishcoarseprop2

```

#### Fine

```{r}

fishnicefine <- rep(c("Callionymiformes",
                      "Carangiformes",
                      "Clupeiformes",
                      "Gadiformes",
                      "Gobiiformes",
                      "Cottoidei",
                      "Percoidei",
                      "Scorpaenoidei",
                      "Uranoscopoidei",
                      "Pleuronectiformes"), each = 10)

Fishfine$fishnice <- fishnicefine

Fishfine <- Fishfine[Fishfine$name %notin% c("Benthos", "Phyto"),]

fishfine_levels <- rep(names(sort(tapply(Fishfine$mean, Fishfine$fishnice, sum), decreasing = TRUE)), each = 8)
Fishfine$fishnice <- factor(Fishfine$fishnice, levels = rev(unique(fishfine_levels)))

Fishfine$prey   <- factor(Fishfine$name, levels = c("Zoo", "SPOM", "SOM", "Biv", "Crust", "Poly", "Other", "Fish"), labels = c("Zooplankton", "SPOM", "SOM", "Bivalves","Crustaceans","Polychaetes","Others", "Fish"))

## Shared species only

Fishfinesub <- Fishfine[Fishfine$fishnice %in% sharedspecies,]
Fishfinesub$fishnice <- factor(Fishfinesub$fishnice, levels = rev(sharedspecies))

fishfinesubplot <- ggplot(data = Fishfinesub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity") + 
                 coord_flip() + 
                 scale_fill_viridis_d(option = "viridis") +  
                 scale_y_continuous(expand = expansion(mult = 0), limits = c(0, 0.5)) +
                 labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Food source", title = "Fine") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                           legend.text = element_text(size = 12))

fishfinesubplot

## Proportional subset
fishfineprop2 <- ggplot(data = Fishfinesub, aes(x = fishnice, y = mean, fill = prey)) +
                  geom_bar(stat = "identity", position = "fill") + 
                  coord_flip() + 
                  scale_fill_viridis_d(option = "viridis") + 
                   scale_y_continuous(expand = expansion(mult = 0)) +
                  labs(x = " ", y = expression(paste("proportion of uptake")), fill = "Food source", title = "Fine") +
                  
                  theme_classic()
fishfineprop2

```

#### OWF

```{r}

fishowfnice <- rep(c("Callionymiformes",
                     "Carangiformes",
                     "Clupeiformes",
                     "Gadiformes",
                     "Gobiiformes",
                     "Mulliformes",
                     "Cottoidei",
                     "Percoidei",
                     "Scorpaenoidei",
                     "Uranoscopoidei",
                     "Pleuronectiformes",
                     "Scombriformes",
                     "Zeiformes"), each = 21)

Fishowf$fishnice <- fishowfnice

Fishowf <- Fishowf[Fishowf$name %notin% c("Benthos", "TEPL", "SSed", "Ubiq", "Phyto"),]
fishowf_levels <- rep(names(sort(tapply(Fishowf$mean, Fishowf$fishnice, sum), decreasing = TRUE)), each = 16)
Fishowf$fishnice <- factor(Fishowf$fishnice, levels = rev(unique(fishowf_levels)))
Fishowf$area <- factor(rep(c(rep("Water column", 3) , rep(c("Hard substrate prey", "Soft sediment prey", "Ubiquitous prey"), each = 4), "Water column"), 13), levels = c("Water column", "Hard substrate prey", "Soft sediment prey", "Ubiquitous prey"))

Fishowf$prey   <- factor(rep(c("Zoo", "SPOM", "SOM", "Biv", "Crust", "Poly", "Other", "Biv", "Crust", "Poly", "Other", "Biv", "Crust", "Poly", "Other", "Fish"), 13), levels = c("Zoo", "SPOM", "SOM", "Biv", "Crust", "Poly", "Other", "Fish"), labels = c("Zooplankton", "SPOM", "SOM", "Bivalves","Crustaceans","Polychaetes","Others", "Fish"))

## Only shared species plots

Fishowfsub <- Fishowf[Fishowf$fishnice %in% sharedspecies,]
Fishowfsub$fishnice <- factor(Fishowfsub$fishnice, levels = rev(sharedspecies))

### Absolute flows
#### Single panel
fishowfsubplot2 <- ggplot(data = Fishowfsub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity") + 
                 coord_flip() + 
                 scale_fill_viridis_d(option = "viridis") + 
                 scale_y_continuous(expand = expansion(mult = 0), limits = c(0, 0.5)) +
                 labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Food source", title = "OWF") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                           legend.text = element_text(size = 12))

fishowfsubplot2

#### 4 panels absolute flows
fishowfsubplot <- ggplot(data = Fishowfsub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity") + 
                 coord_flip() + 
                 scale_fill_viridis_d(option = "viridis") + 
                 facet_grid(~area) + #, scales = "free_x") + 
                 labs(x = " ", y = expression(paste("mmol C m"^"-2", " d"^"-1")), fill = "Food source", title = "OWF foodweb") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                          legend.text = element_text(size = 12))

fishowfsubplot

### Relative flows
#### Single panel
fishowfpropsub  <- ggplot(data = Fishowfsub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity", position = "fill") + 
                 coord_flip() + 
                scale_y_continuous(expand = expansion(mult = 0)) +
                 scale_fill_viridis_d(option = "viridis") + 
                 labs(x = " ", y = expression(paste("proportion of uptake")), fill = "Food source", title = "OWF foodweb") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                          legend.text = element_text(size = 12))


fishowfpropsub

#### 4 panels
fishowfpropsub2 <- ggplot(data = Fishowfsub, aes(x = fishnice, y = mean, fill = prey)) +
                 geom_bar(stat = "identity", position = "fill") + 
                 coord_flip() + 
                 scale_fill_viridis_d(option = "viridis") + 
                 facet_grid(~area) + 
                 labs(x = " ", y = expression(paste("proportion of uptake")), fill = "Food source", title = "OWF") +
                    theme_classic() + 
                     theme(axis.text.x = element_text(size = 12),
                           axis.text.y = element_text(size = 12),
                           axis.title  = element_text(size = 14),
                           legend.title = element_text(size = 12),
                          legend.text = element_text(size = 12))


fishowfpropsub2

```

##### Combine figures

```{r}

# Absolute uptakes
library(patchwork)
layout <- "111222333
           111222333
           111222333
           444444444
           444444444"

Fishuptake <- fishcoarsesubplot + fishfinesubplot + fishowfsubplot2 + fishowfsubplot
Fishuptake <- Fishuptake + plot_layout(design = layout, guides = "collect") + plot_annotation(tag_levels = 'A')
Fishuptake

ggsave("./paper_figures_tables/figures/Figure4_fishuptake_totalvalues.png", height = 10, width = 12)


# Proportional uptake
Fishuptakeprop <- fishcoarseprop2 + fishfineprop2 + fishowfpropsub + fishowfpropsub2
Fishuptakeprop <- Fishuptakeprop + plot_layout(design = layout, guides = "collect") + plot_annotation(tag_levels = 'A')
Fishuptakeprop

ggsave("./paper_figures_tables/figures/Figure4_fishuptake_proportional.pdf", height = 10, width = 12)

```

### Fish diet stats=istics

```{r}

library(readr)
library(dplyr)

perform_t_test <- function(group1, group2) {
  mean1 <- group1$mean_proportion
  std1  <- group1$mean_sd
  n1    <- 10000

  mean2 <- group2$mean_proportion
  std2  <- group2$mean_sd
  n2    <- 10000

  t_stat <- (mean1 - mean2) / sqrt((std1^2 / n1) + (std2^2 / n2))
  df <- ((std1^2 / n1) + (std2^2 / n2))^2 / (((std1^2 / n1)^2 / (n1 - 1)) + ((std2^2 / n2)^2 / (n2 - 1)))
  p_value <- 2 * pt(-abs(t_stat), df)

  return(list(t_stat = t_stat, df = df, p_value = p_value))
}

fishstats <- read_delim("fishstats.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)

# Get unique Foodsources
foodsources <- unique(fishstats$Foodsource)

# Initialize a list to store results
results <- list()

for(i in unique(fishstats$Fish)){
  
  sub <- fishstats[fishstats$Fish == i,]
  
  for (foodsource in foodsources) {
    
    subset_data <- sub %>% filter(Foodsource == foodsource)
    foodwebs <- unique(subset_data$Foodweb)
    
    if (length(foodwebs) < 2) next  # Skip if less than 2 groups to compare
    
    dims <- lapply(2, function(y) combn(foodwebs, y))[[1]]
    
    for (j in 1:ncol(dims)) {
      group1 <- subset_data %>% filter(Foodweb == dims[1,j])
      group2 <- subset_data %>% filter(Foodweb == dims[2,j])
        
      test_result <- perform_t_test(group1, group2)
        
      result <- list(
        fish = i,
        foodsource = foodsource,
        foodweb1 = group1$Foodweb,
        foodweb2 = group2$Foodweb,
        t_stat = test_result$t_stat,
        df = test_result$df,
        p_value = test_result$p_value
      )
        
      results <- append(results, list(result))
    }
  }
}


results_tibble <- bind_rows(lapply(results, as_tibble))
print(results_tibble, n = 110)

write.table(results_tibble, "./paper_figures_tables/tables/fishdietstats.txt", quote = FALSE)

```

# Statistics

```{r}

## Load data
load("./finalresults/coarsecflowsmatrixbootstrap.Rdata") # bscoarsecflows
load("./finalresults/coarsefishmatrixbootstrap.Rdata")   # bscoarsefish

load("./finalresults/finecflowsmatrixbootstrap.Rdata")   # bsfinecflows
load("./finalresults/finefishmatrixbootstrap.Rdata")     # bsfinefish

load("./finalresults/owfcflowsmatrixbootstrap.Rdata")    # bsowfcflows
load("./finalresults/owffishmatrixbootstrap.Rdata")      # bsowffish

XYcomparison <- function(Co=NULL, Fi=NULL, Ow=NULL, cutoff=1){
                            n       <- length(Co)
                            Coboot <- Co[sort(runif(n),index.return=TRUE)$ix]
                            Fiboot <- Fi[sort(runif(n),index.return=TRUE)$ix]
                            Owboot <- Ow[sort(runif(n),index.return=TRUE)$ix]
                            
                            CoFiboot <- Coboot / Fiboot
                            CoFi     <-  sum(CoFiboot>cutoff)/length(CoFiboot)
                            CoOwboot <- Coboot / Owboot
                            CoOw     <-  sum(CoOwboot>cutoff)/length(CoOwboot)
                            FiOwboot <- Fiboot / Owboot
                            FiOw     <-  sum(FiOwboot>cutoff)/length(FiOwboot)

                            return(data.frame("Coarse-Fine" = CoFi,
                                              "Coarse-OWF"  = CoOw,
                                              "Fine-OWF"    = FiOw))
}

# "How often is it larger?"
## Main fluxes
flxes <- c("Zoo->DIC", "Fish->DIC", "Jelly->DIC", "SedBac->DIC") 

fluxcomps2 <- NULL
for(i in seq_along(flxes)){
  
  flow <- flxes[i]
  
  out <- XYcomparison(Co = bscoarsecflows[,flow],
                      Fi = bsfinecflows[,flow],
                      Ow = bsowfcflows[,flow])
  rownames(out) <- flow
  fluxcomps2 <- rbind(fluxcomps2, out)
}

fluxcomps2 <- cbind(fluxcomps2*100)



fluxcomps <- NULL
for(i in 1:41){
  
  out <- XYcomparison(Co = bscoarsecflows[,i],
                      Fi = bsfinecflows[,i],
                      Ow = bsowfcflows[,i])
  rownames(out) <- colnames(bscoarsecflows)[i]
  fluxcomps <- rbind(fluxcomps, out)
}

fluxcomps <- cbind("Coarse" = round(restabcoarse$mean[1:41], 4), 
                   "Fine"   = round(restabfine$mean[1:41], 4), 
                   "OWF"    = round(restabowf$mean[1:41], 4), fluxcomps*100)


## Indices
indcomps <- NULL
for(i in 1:17){
  
  out <- XYcomparison(Co = netindcoarse[,i],
                      Fi = netindfine[,i],
                      Ow = netindowf[,i])
  rownames(out) <- colnames(netindcoarse)[i]
  indcomps <- rbind(indcomps, out)
}

indcomps <- cbind("Coarse" = round(NICOARSE$mean[1:17],4), 
                  "Fine"   = round(NIfine$mean[1:17],4), 
                  "OWF"    = round(NIowf_2$mean[1:17],4), indcomps*100)

## Fish diets
bscoarsefish$row_id <- rownames(bscoarsefish)
long_dfcoarse <- pivot_longer(bscoarsefish, 
                           cols = -row_id, 
                           names_to = c("Fish", "Prey"), 
                           names_sep = "_")
wide_dfcoarse <- pivot_wider(long_dfcoarse, 
                          names_from = row_id, 
                          values_from = value)

bsfinefish$row_id <- rownames(bsfinefish)
long_dffine <- pivot_longer(bsfinefish, 
                           cols = -row_id, 
                           names_to = c("Fish", "Prey"), 
                           names_sep = "_")
wide_dffine <- pivot_wider(long_dffine, 
                          names_from = row_id, 
                          values_from = value)

bsowffish$row_id <- rownames(bsowffish)

long_dfowf <- pivot_longer(bsowffish, 
                           cols = -row_id, 
                           names_to = c("Fish", "Prey"), 
                           names_sep = "_")

long_dfowf <- long_dfowf %>%
  mutate(Prey = case_when(
    Prey %in% c("Biv", "Crust", "Poly", "Other") ~ Prey,
    grepl("Biv", Prey) ~ "Biv",
    grepl("Crust", Prey) ~ "Crust",
    grepl("Poly", Prey) ~ "Poly",
    grepl("Other", Prey) ~ "Other",
    TRUE ~ Prey
  )) %>%
  group_by(Fish, Prey, row_id) %>%
  summarise(value = sum(value, na.rm = TRUE), .groups = 'drop')

# Desired order of prey types
desired_order <- c("Phyto", "Zoo", "SPOM", "SOM", "Benthos", "Biv", "Crust", "Poly", "Other", "Fish")

# Ensure "Prey" column matches the desired levels
long_dfowf <- long_dfowf %>%
  mutate(Prey = factor(Prey, levels = desired_order))

# Filter out rows where "Prey" is NA (which would be the dropped levels)
long_dfowf <- long_dfowf %>%
  filter(!is.na(Prey))

# Step 3: Pivot back to wide format with the desired order
wide_dfowf <- pivot_wider(long_dfowf, 
                           names_from = row_id, 
                           values_from = value)
levels(wide_dfowf$Prey)[10] <- "Pisc"

# Mega_dataframe
merged_df <- full_join(wide_dfcoarse, wide_dffine, by = c("Fish", "Prey"), suffix = c("_coarse", "_fine"))

# Merge the result with df3
merged_df <- full_join(merged_df, wide_dfowf, by = c("Fish", "Prey"), suffix = c("", "_owf"))

# Run permanova and simper.

fish <- c("CALLIO", "CARANG", "GADIFO", "GOBIFO", "COTTOI", "PERCOI", "SCORPA", "AMMODY", "PLEURO")

permlist2 <- list(NULL)
simplist2 <- list(NULL)

for(i in seq_along(fish)){
  
  fishsp <- fish[i]
  sub <- t(subset(merged_df, Fish == fishsp)[,-c(1,2)])
  colnames(sub) <- desired_order
  sub <- sub[,-5]
  seqrow <- seq(1, nrow(sub), by = 100)
  sub <- sub[seqrow,]
  sub <- decostand(sub, "total", margin = 1)
  fws <- c(rep("Coarse", 9950),rep("Fine", 9950),rep("OWF", 12250))[seqrow]
  sub.env <- data.frame("FW" = c(fws), "this" = rep("a", length(fws)))
  
  sub_braycurtis <- vegdist(sub, method = "bray")

  # Perform PERMANOVA
  permanova_result <- pairwise.adonis2(sub_braycurtis~FW, data = sub.env)
  # print(permanova_result)
  
  # Perform SIMPER
  simper_result <- simper(sub, sub.env$FW, permutations = 999)
  # print(simper_result)
  
  permlist2[[i]] <- permanova_result
  simplist2[[i]] <- simper_result
  names(permlist2)[i] <- fishsp
  names(simplist2)[i] <- fishsp
}

save(file = "./finalresults/fishpermanovacomparison.rda", permlist2)
save(file = "./finalresults/fishsimpercomparison.rda", simplist2)

```

# Foodweb indices

## Network indices

```{r, networkindcestable, echo = FALSE}

indtab <- cbind(NICOARSE$mean, NIfine$mean, NIowf_2$mean, 
                   NICOARSE$stdev, NIfine$stdev, NIowf_2$stdev)
colnames(indtab) <- c("Coarse mean", "Fine mean", "OWF mean",
                      "Coarse std" , "Fine std" , "OWF std")
rownames(indtab) <- rownames(NICOARSE)
knitr::kable(indtab, caption = "Network indices", digits = 3)

write.table(indtab, "./paper_figures_tables/tables/trophic_indices.txt", quote = FALSE)

```
