---
title: "foodweb_780"
author: "Emil De Borger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  markdown: 
    wrap: 72
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---

# Description

-   Runs the foodweb as specified in `/final_versions/fine.input`.

-   Links between groups based on literature research.

-   Ldei: Solves a linear inverse model using least distance programming
    (i.e. minimizes sum of squared unknowns). $\min(∑ {Cost_i*x_i}^2)$
    Subject to equalities and inequalities: $Ax = B$ $Gx>=H$

-   ldei: Solves *underdetermined* inverse problem $\min(∑ {x_i}^2)$
    subject to equalities and inequalities: $Ax = B$ $Gx>=H$
    Underdetermined: number of independent equations \< number of
    unknowns.

```{r setup, include=FALSE}

# Packages 
require(LIM)
require(splus2R)
require(NetIndices)
require(MASS)
require(parallel)

# Files
File.fine <- "./final_versions/fine.input"

```


# Reading LIM and run ranges

### Read LIM

```{r}

readLIM.fine  <- LIM::Read(file = File.fine, verbose = TRUE, checkLinear = TRUE)

```

# Solving LIM

### Single solution and ranges

```{r}

# Ranges and solution
readLIM.fine  <- LIM::Read(file = File.fine, verbose = TRUE, checkLinear = TRUE)
LIM.fine      <- Setup(readLIM.fine)
Solldeifine   <- Ldei(LIM.fine, verbose = T)
Rangesfine    <- Xranges(LIM.fine, central = T, ispos = T)
varrangesfine <- Varranges(LIM.fine)

# Check validity of solution
any((LIM.fine$A %*% Solldeifine$X - LIM.fine$B)>1e-8)
any((LIM.fine$G %*% Solldeifine$X - LIM.fine$H)<(-1E-8))


save(readLIM.fine , file = "./finalresults/readlimfine.rda")
save(LIM.fine     , file = "./finalresults/limfine.rda")
save(Solldeifine  , file = "./finalresults/solldeifine.rda")
save(Rangesfine   , file = "./finalresults/rangesfine.rda")
save(varrangesfine, file = "./finalresults/varrangesfine.rda")

```

### Cluster computing

- Evaluated online on NIOZ BIOINFORMATICS server

### Load .rda elements

```{r label, options}

load(file = "./780_export/MCMCfine.rda")
XFine <- mcExtract(mcmcfine)

```

# Analysis of fluxes

### Mean-sd of flows.

```{r}

finalmatrix <- XFine
LIM         <- LIM.fine
readLIM     <- readLIM.fine
variranges  <- varrangesfine

# Mean + SD of solutions.
### Get mean±std
meanvalues  <- cbind(LIM$Unknowns, colMeans(finalmatrix))
standarddev <- cbind(LIM$Unknowns, sqrt(diag(var(finalmatrix))))

### Add to dataframe
minimum <- apply(finalmatrix, 2, min, na.rm = TRUE)
maximum <- apply(finalmatrix, 2, max, na.rm = TRUE)

flow       <- meanvalues[,1]
mean       <- as.numeric(meanvalues[,2])
std        <- as.numeric(standarddev[,2])
Flows.Fine <- data.frame(flow, mean, std, minimum, maximum)

### Save as excel sheet.
write.csv(Flows.Fine, paste("./finalresults/Flows_fine_iso.csv"))
### The Flows data frame is saved as .Rdata file
save(Flows.Fine, file = paste0("./finalresults/Flows_fine_iso.Rdata"))

### Get Flowmatrix with Bayesian solution.
FM.Fine <- getFlowMatrix(originalFM = LIM$Flowmatrix, 
                        flows      = readLIM$flows , 
                        answers    = Flows.780[,"mean"])


# Mean + SD of variable estimates
Vals      <- data.frame(variranges)
Vals$mean <- numeric(LIM$NVariables)
Vals$std  <- numeric(LIM$NVariables)
  
vareq      <- readLIM$vars # matrix which defines the variable equations
parvec     <- readLIM$pars$val # vector with parameter values
flowvec    <- as.numeric(meanvalues[,2]) # vector with mean flow values
flowstdvec <- as.numeric(standarddev[,2]) # vector with flow standard deviations

for (j in 1:LIM$NVariables) {
  # refresh vector with mean and std values
  varvec <- Vals$mean
  varstdvec <- Vals$std
  
  # Get subset with the same equation nr.
  subset <- vareq[vareq$nr == j,] 
    
  # Take parameter, variable or flow nr from subset to use as index. 
  # Use index to find the corresponding values.
  # Multiply the values by 'val' which is the coefficient (like 1 or -1) and sum them.
  sum <- 
    sum(parvec[subset$par1]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par2]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par3]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par4]*subset$val, na.rm = TRUE) +
    sum(varvec[subset$var]*subset$val , na.rm = TRUE) +
    sum(flowvec[subset$flow]*subset$val, na.rm = TRUE)  
  
  # Use index to find corresponding standard deviations.
  # Sum squared standard deviations and take the square root.
  stddev <- 
    sqrt(
      sum(flowstdvec[subset$flow]^2, na.rm = TRUE) +
        sum(varstdvec[subset$var]^2, na.rm = TRUE)
    )
  
  # Add values to data frame.
  Vals$mean[j] = sum 
  Vals$std[j]  = stddev
}
  
# The Vals data frame is saved as .Rdata file.
Vals_Fine <- Vals
save(Vals_Fine, file = paste0("./finalresults/vals_fine_iso.Rdata"))

# Clean up memory
rm(finalmatrix, readLIM  , LIM        ,
   meanvalues , mean     , standarddev, 
   std        , stddev   , flow       , 
   maximum    , minimum  , sum        ,
   parvec     , varstdvec, flowstdvec , 
   vareq      , flowvec  , Vals       ,
   variranges , subset)

```

### Summary of fluxes

```{r}

Fish        <- c(LIM.fine$Components$name[1:10])  #String with fish.
Benthos     <- c(LIM.fine$Components$name[12:40]) #String with benthos.
bivalves    <- c(LIM.fine$Components$name[19:22])  
crustacea   <- c(LIM.fine$Components$name[12:18]) 
polychaetes <- c(LIM.fine$Components$name[28:34]) 
others      <- c(LIM.fine$Components$name[c(23:27, 35:40)]) 

phytobenth <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", Benthos)))
zoobenth   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", Benthos)))
spombenth  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", Benthos)))
sombenth   <- which(Flows.Fine$flow %in% c(paste0("SOM->", Benthos)))
benthbenth <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, Benthos, sep="->"))))

phytobiv <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", bivalves)))
zoobiv   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", bivalves)))
spombiv  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", bivalves)))
sombiv   <- which(Flows.Fine$flow %in% c(paste0("SOM->", bivalves)))
benthbiv <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, bivalves, sep="->"))))

phytocrust <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", crustacea)))
zoocrust   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", crustacea)))
spomcrust  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", crustacea)))
somcrust   <- which(Flows.Fine$flow %in% c(paste0("SOM->", crustacea)))
benthcrust <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, crustacea, sep="->"))))

phytopoly <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", polychaetes)))
zoopoly   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", polychaetes)))
spompoly  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", polychaetes)))
sompoly   <- which(Flows.Fine$flow %in% c(paste0("SOM->", polychaetes)))
benthpoly <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, polychaetes, sep="->"))))

phytooth <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", others)))
zoooth   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", others)))
spomoth  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", others)))
somoth   <- which(Flows.Fine$flow %in% c(paste0("SOM->", others)))
benthoth <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, others, sep="->"))))

phytofish  <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", Fish))) 
zoofish    <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", Fish))) 
spomfish   <- which(Flows.Fine$flow %in% c(paste0("SPOM->", Fish))) 
somfish    <- which(Flows.Fine$flow %in% c(paste0("SOM->", Fish))) 
benthofish <- which(Flows.Fine$flow %in% c(paste0("Benthos->", Fish))) 
bivfish    <- which(Flows.Fine$flow %in% c(levels(interaction(bivalves, Fish, sep="->")))) 
crusfish   <- which(Flows.Fine$flow %in% c(levels(interaction(crustacea, Fish, sep="->")))) 
polyfish   <- which(Flows.Fine$flow %in% c(levels(interaction(polychaetes, Fish, sep="->")))) 
othfish    <- which(Flows.Fine$flow %in% c(levels(interaction(others, Fish, sep="->"))))

cflows    <- c("OM deposition"         ,
               "Fish respiration"      ,
               "Jellyfish respiration" , 
               "Bacterial respiration" ,
               "Macrofauna respiration",
               "Sediment respiration"  ,
               "Water respiration"     , #no phytoplankton
               "Total respiration"     , #no phytoplankton
               "Burial"                ,
               "Total export"          ,
               "phytoplankton uptake macrofauna",
               "zooplankton uptake macrofauna"  ,
               "SOM uptake macrofauna"          ,
               "SPOM uptake macrofauna"         ,
               "Total uptake macrofauna"        ,
               "SOM uptake bacteria"            ,
               "SPOM uptake bacteria"           , 
               "Uptake water bivalves"          ,
               "Uptake water crustaceans"       ,
               "Uptake water polychaetes"       ,
               "Uptake water others"            ,
               "Uptake SOM bivalves"            ,
               "Uptake SOM crustaceans"         ,
               "Uptake SOM polychaetes"         ,
               "Uptake SOM others"              ,
               "Total carbon outflow"           ,
               "Total carbon inflow"            ,
               "Phyto->Zoo",
               "Zoo->SPOM",
               "Phyto->SPOM",
               "Zoo->Fish",
               "SPOM->Fish",
               "Fish->SPOM",
               "WatBac->DIC",
               "SPOM->WatBac",
               "WatBac->SPOM",
               "Zoo->Jelly",
               "Jelly->SPOM",
               "SOM->SedBac",
               "SedBac->SOM",
               "SOM->Burial",
               "SedBac->Burial",
               "Benthos->Fish",
               "Zoo->DIC",
               "Fish->DIC",
               "Jelly->DIC",
               "SedBac->DIC",
               "Benthos->DIC",
               "DIC->Phyto",
               "Benthos->SOM",
               "Phyto->Benthos",
               "Zoo->Benthos",
               "SPOM->Benthos",
               "SOM->Benthos",
               "Benthos->Benthos",
               "Phyto->Bivalves",
               "Zoo->Bivalves",
               "SPOM->Bivalves",
               "SOM->Bivalves",
               "Benthos->Bivalves",
               "Phyto->Crustaceans",
               "Zoo->Crustaceans",
               "SPOM->Crustaceans",
               "SOM->Crustaceans",
               "Benthos->Crustaceans",
               "Phyto->Polychaetes",
               "Zoo->Polychaetes",
               "SPOM->Polychaetes",
               "SOM->Polychaetes",
               "Benthos->Polychaetes",
               "Phyto->Others",
               "Zoo->Others",
               "SPOM->Others",
               "SOM->Others",
               "Benthos->Others",
               "Phyto->Export",
               "Zoo->Export",
               "Fish->Export",
               "Jelly->Export",
               "Benthos->Export"
)

restabfine <- data.frame(name = cflows, mean = NA, std = NA)

ii <- list(grep("SPOM->SOM", Flows.Fine$flow), # OMdepo OK
           c(449:458) ,         # Fishresp OK
           c(459)     ,         # Jelresp OK
           c(489:490) ,         # Bactresp OK
           c(460:488) ,         # Macresp OK
           c(460:489) ,         # Sedresp OK
           c(449:459, 490:491), # Watresp OK No phytoplankton
           c(449:491)     ,     # Totresp OK No phytoplankton
           c(536)         ,     # totbur OK
           c(492:535)     ,     # totexp OK
           grep("PHYTOPLANKT->", Flows.Fine$flow)[c(1:6)]  , # Phyto upt. macrofauna
           grep("ZOOPLANKT->", Flows.Fine$flow)[c(12:22)]  , # Zoo upt. macrofauna
           grep("SOM->", Flows.Fine$flow)[c(3:26)]         , # SOM upt. macrofauna
           grep("SPOM->", Flows.Fine$flow)[c(3:16)]        , # SPOM upt. macrofauna
           c(grep("PHYTOPLANKT->", Flows.Fine$flow)[c(1:6)], # Total upt. macrofauna
             grep("ZOOPLANKT->", Flows.Fine$flow)[c(12:22)], 
             grep("SOM->", Flows.Fine$flow)[c(3:26)]       ,
             grep("SPOM->", Flows.Fine$flow)[c(3:16)])     ,
           grep("SOM->SEDBAC" , Flows.Fine$flow)                  , # SOM uptake bacteria
           grep("SPOM->WATBAC", Flows.Fine$flow)                  , # SPOM uptake bacteria
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Fine$flow)[c(21:28)]       , # Water uptake bivalves
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Fine$flow)[c(14:20)]       , # Water uptake crusties
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Fine$flow)[c(35:40)]       , # Water uptake polychaetes
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Fine$flow)[c(29:34, 41:44)], # Water uptake others
           grep("SOM->", Flows.Fine$flow)[c(10:12)]        , # Uptake SOM bivalves
           grep("SOM->", Flows.Fine$flow)[c(3:9)]          , # Uptake SOM crustaceans
           grep("SOM->", Flows.Fine$flow)[c(16:21)]       , # Uptake SOM polychaetes
           grep("SOM->", Flows.Fine$flow)[c(13:15, 22:26)], # Uptake SOM others
           c(449:536)                                    , # Tot C outflow burial + export + respiration (??)
           grep("DIC->PHYTOPLANKT", Flows.Fine$flow)      , # Tot C inflow
           grep("PHYTOPLANKT->ZOOPLANKT", Flows.Fine$flow), # Phyto->Zoo
           grep("ZOOPLANKT->SPOM", Flows.Fine$flow)       , # Zoo->SPOM
           grep("PHYTOPLANKT->SPOM", Flows.Fine$flow)     , # Phyto->Fish
           grep("ZOOPLANKT->", Flows.Fine$flow)[c(1:10)]  , # zoo->Fish
           grep("SPOM->", Flows.Fine$flow)[c(1)]          , # SPOM->Fish
           grep("->SPOM", Flows.Fine$flow)[c(2:11)]       , # Fish->SPOM
           grep("WATBAC->DIC", Flows.Fine$flow)           , # watbac->DIC
           grep("SPOM->WATBAC", Flows.Fine$flow)          , # SPOM->WATBAC
           grep("WATBAC->SPOM", Flows.Fine$flow)          , # watbac -> SPOM
           grep("ZOOPLANKT->JELLY", Flows.Fine$flow)      , # zooplankt->Jelly
           grep("JELLY->SPOM", Flows.Fine$flow)           , # jelly->SPOM
           grep("SOM->SEDBAC", Flows.Fine$flow)           , # SOM->Sedbac
           grep("SEDBAC->SOM", Flows.Fine$flow)           , # sedbac -> SOM
           grep("SOM->BUR", Flows.Fine$flow)              , # SOM->Burial
           grep("SEDBAC->BUR", Flows.Fine$flow)           , # Sedbac -> Burial
           c(2:21, 25:31, 42:58, 60:81, 86:105, 108:120, 130:135, 142:145, 149:171, 173, 175:178), # Benthos -> Fish
           grep("ZOOPLANKT->DIC", Flows.Fine$flow)        , # Zoo->DIC
           grep("->DIC", Flows.Fine$flow)[1:10]            , # Fish->DIC
           grep("->DIC", Flows.Fine$flow)[11]             , # jelly->DIC
           grep("SEDBAC->DIC", Flows.Fine$flow)           , # Sedbac->DIC
           grep("->DIC", Flows.Fine$flow)[12:40]          , # Benthos->DIC
           grep("DIC->PHYTOPLANKT", Flows.Fine$flow)      , # DIC->Phyto
           grep("->SOM", Flows.Fine$flow)[3:31],             # Benthos->SOM
           phytobenth                         ,
           zoobenth                           ,
           spombenth                          ,
           sombenth                           ,
           benthbenth                         ,
           phytobiv                           ,
           zoobiv                             ,
           spombiv                            ,
           sombiv                             ,
           benthbiv                           ,
           phytocrust                         ,
           zoocrust                           ,
           spomcrust                          ,
           somcrust                           ,
           benthcrust                         ,
           phytopoly                          ,
           zoopoly                            ,
           spompoly                           ,
           sompoly                            ,
           benthpoly                          ,
           phytooth                           ,
           zoooth                             ,
           spomoth                            ,
           somoth                             ,
           benthoth                           ,
           c(534)                             ,
           c(535)                             ,
           c(492:501)                         ,
           c(502)                             ,
           c(503:531)
           )

for(i in 1:length(ii)){
  restabfine[i,"mean"] <- sum(Flows.Fine$mean[ii[[i]]])
  restabfine[i,"std"]  <- stdfromstd(Flows.Fine$std[ii[[i]]])
  restabfine[i,"min"]  <- sum(Flows.Fine$minimum[ii[[i]]])
  restabfine[i,"max"]  <- sum(Flows.Fine$maximum[ii[[i]]])
}

knitr::kable(restabfine)

save(restabfine, file = paste0("./finalresults/restab_fine_iso.Rdata"))
write.csv(restabfine, file = "./finalresults/restabfine.csv", row.names = FALSE)

#### Fish

Fishfine <- NULL

for(i in Fish){
  
  ii <- list(
  phy   <- which(Flows.Fine$flow %in% c(paste0("PHYTOPLANKT->", i))),
  zoo   <- which(Flows.Fine$flow %in% c(paste0("ZOOPLANKT->", i))),
  spom  <- which(Flows.Fine$flow %in% c(paste0("SPOM->", i))),
  som   <- which(Flows.Fine$flow %in% c(paste0("SOM->", i))),
  benth <- which(Flows.Fine$flow %in% c(levels(interaction(Benthos, i, sep="->")))),
  biv   <- which(Flows.Fine$flow %in% c(levels(interaction(bivalves, i, sep="->")))),
  cru   <- which(Flows.Fine$flow %in% c(levels(interaction(crustacea, i, sep="->")))),
  pol   <- which(Flows.Fine$flow %in% c(levels(interaction(polychaetes, i, sep="->")))),
  oth   <- which(Flows.Fine$flow %in% c(levels(interaction(others, i, sep="->")))), 
  pisc  <- which(Flows.Fine$flow %in% c(levels(interaction(Fish, i, sep="->"))))
  )
  
  nms <- c("Phyto", "Zoo", "SPOM", "SOM", "Benthos", "Biv", "Crust", "Poly", "Other", "Fish")
  new <- data.frame(name = nms, mean = NA, std = NA, min = NA, max = NA)

  for(j in 1:length(ii)){
  new[j, "Fish"] <- i
  new[j,"mean"] <- sum(Flows.Fine$mean[ii[[j]]])
  new[j,"std"]  <- stdfromstd(Flows.Fine$std[ii[[j]]])
  new[j,"min"]  <- sum(Flows.Fine$minimum[ii[[j]]])
  new[j,"max"]  <- sum(Flows.Fine$maximum[ii[[j]]])
  }
  
  Fishfine <- rbind(Fishfine, new)
  
}

save(Fishfine     , file = paste0("./finalresults/fish_fine_iso.Rdata"))
write.csv(Fishfine, file = "./finalresults/fishfine.csv", row.names = FALSE)

```

# Matrix for bootstrapping comparison

```{r}

bsfine <- XFine
colnames(bsfine) <- Flows.Fine$flow

ii <- list(grep("SPOM->SOM", colnames(bsfine)), # OMdepo OK
           c(449:458) ,         # Fishresp OK
           c(459)     ,         # Jelresp OK
           c(489:490) ,         # Bactresp OK
           c(460:488) ,         # Macresp OK
           c(460:489) ,         # Sedresp OK
           c(449:459, 490:491), # Watresp OK No phytoplankton
           c(449:491)     ,     # Totresp OK No phytoplankton
           c(536)         ,     # totbur OK
           c(492:535)     ,     # totexp OK
           grep("PHYTOPLANKT->", colnames(bsfine))[c(1:6)]  , # Phyto upt. macrofauna
           grep("ZOOPLANKT->", colnames(bsfine))[c(12:22)]  , # Zoo upt. macrofauna
           grep("SOM->", colnames(bsfine))[c(3:26)]         , # SOM upt. macrofauna
           grep("SPOM->", colnames(bsfine))[c(3:16)]        , # SPOM upt. macrofauna
           c(grep("PHYTOPLANKT->", colnames(bsfine))[c(1:6)], # Total upt. macrofauna
             grep("ZOOPLANKT->", colnames(bsfine))[c(12:22)], 
             grep("SOM->", colnames(bsfine))[c(3:26)]       ,
             grep("SPOM->", colnames(bsfine))[c(3:16)])     ,
           grep("SOM->SEDBAC" , colnames(bsfine))                  , # SOM uptake bacteria
           grep("SPOM->WATBAC", colnames(bsfine))                  , # SPOM uptake bacteria
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bsfine))[c(21:28)]       , # Water uptake bivalves
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bsfine))[c(14:20)]       , # Water uptake crusties
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bsfine))[c(35:40)]       , # Water uptake polychaetes
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bsfine))[c(29:34, 41:44)], # Water uptake others
           grep("SOM->", colnames(bsfine))[c(10:12)]        , # Uptake SOM bivalves
           grep("SOM->", colnames(bsfine))[c(3:9)]          , # Uptake SOM crustaceans
           grep("SOM->", colnames(bsfine))[c(16:21)]       , # Uptake SOM polychaetes
           grep("SOM->", colnames(bsfine))[c(13:15, 22:26)], # Uptake SOM others
           c(449:536)                                    , # Tot C outflow burial + export + respiration (??)
           grep("DIC->PHYTOPLANKT", colnames(bsfine))      , # Tot C inflow
           grep("PHYTOPLANKT->ZOOPLANKT", colnames(bsfine)), # Phyto->Zoo
           grep("ZOOPLANKT->SPOM", colnames(bsfine))       , # Zoo->SPOM
           grep("PHYTOPLANKT->SPOM", colnames(bsfine))     , # Phyto->Fish
           grep("ZOOPLANKT->", colnames(bsfine))[c(1:10)]  , # zoo->Fish
           grep("SPOM->", colnames(bsfine))[c(1)]          , # SPOM->Fish
           grep("->SPOM", colnames(bsfine))[c(2:11)]       , # Fish->SPOM
           grep("WATBAC->DIC", colnames(bsfine))           , # watbac->DIC
           grep("SPOM->WATBAC", colnames(bsfine))          , # SPOM->WATBAC
           grep("WATBAC->SPOM", colnames(bsfine))          , # watbac -> SPOM
           grep("ZOOPLANKT->JELLY", colnames(bsfine))      , # zooplankt->Jelly
           grep("JELLY->SPOM", colnames(bsfine))           , # jelly->SPOM
           grep("SOM->SEDBAC", colnames(bsfine))           , # SOM->Sedbac
           grep("SEDBAC->SOM", colnames(bsfine))           , # sedbac -> SOM
           grep("SOM->BUR", colnames(bsfine))              , # SOM->Burial
           grep("SEDBAC->BUR", colnames(bsfine))           , # Sedbac -> Burial
           c(2:21, 25:31, 42:58, 60:81, 86:105, 108:120, 130:135, 142:145, 149:171, 173, 175:178), # Benthos -> Fish
           grep("ZOOPLANKT->DIC", colnames(bsfine))        , # Zoo->DIC
           grep("->DIC", colnames(bsfine))[1:10]            , # Fish->DIC
           grep("->DIC", colnames(bsfine))[11]             , # jelly->DIC
           grep("SEDBAC->DIC", colnames(bsfine))           , # Sedbac->DIC
           grep("->DIC", colnames(bsfine))[12:40]          , # Benthos->DIC
           grep("DIC->PHYTOPLANKT", colnames(bsfine))      , # DIC->Phyto
           grep("->SOM", colnames(bsfine))[3:31],             # Benthos->SOM
           phytobenth                         ,
           zoobenth                           ,
           spombenth                          ,
           sombenth                           ,
           benthbenth                         ,
           phytobiv                           ,
           zoobiv                             ,
           spombiv                            ,
           sombiv                             ,
           benthbiv                           ,
           phytocrust                         ,
           zoocrust                           ,
           spomcrust                          ,
           somcrust                           ,
           benthcrust                         ,
           phytopoly                          ,
           zoopoly                            ,
           spompoly                           ,
           sompoly                            ,
           benthpoly                          ,
           phytooth                           ,
           zoooth                             ,
           spomoth                            ,
           somoth                             ,
           benthoth                           ,
           c(534)                             ,
           c(535)                             ,
           c(492:501)                         ,
           c(502)                             ,
           c(503:531)
)

bsfinecflows <- data.frame(matrix(data = NA, nrow = 9950))

for(i in 1:length(ii)){
  bsfinecflows <- cbind(bsfinecflows, rowSums(cbind(bsfine[,ii[[i]]], rep(0, 9950))))
}

bsfinecflows <- bsfinecflows[,-1]
colnames(bsfinecflows) <- cflows

#################################

bsfinefish <- data.frame(matrix(data = NA, nrow = 9950))
namevec <- NULL

for(i in Fish){
  
  ii <- list(
  phy   <- which(colnames(bsfine) %in% c(paste0("PHYTOPLANKT->", i))),
  zoo   <- which(colnames(bsfine) %in% c(paste0("ZOOPLANKT->", i))),
  spom  <- which(colnames(bsfine) %in% c(paste0("SPOM->", i))),
  som   <- which(colnames(bsfine) %in% c(paste0("SOM->", i))),
  benth <- which(colnames(bsfine) %in% c(levels(interaction(Benthos, i, sep="->")))),
  biv   <- which(colnames(bsfine) %in% c(levels(interaction(bivalves, i, sep="->")))),
  cru   <- which(colnames(bsfine) %in% c(levels(interaction(crustacea, i, sep="->")))),
  pol   <- which(colnames(bsfine) %in% c(levels(interaction(polychaetes, i, sep="->")))),
  oth   <- which(colnames(bsfine) %in% c(levels(interaction(others, i, sep="->")))), 
  pisc  <- which(colnames(bsfine) %in% c(levels(interaction(Fish, i, sep="->"))))
  )
  
  nms <- paste0(i, "_", c("Phyto", "Zoo", "SPOM", "SOM", "Benthos", "Biv", "Crust", "Poly", "Other", "Pisc"))

  for(j in 1:length(ii)){
    bsfinefish <- cbind(bsfinefish, rowSums(bsfine[,ii[[j]], drop = FALSE]))
  }
  
  namevec <- c(namevec, nms)
  
}

bsfinefish <- bsfinefish[,-1]
colnames(bsfinefish) <- namevec

save(bsfinecflows     , file = paste0("./finalresults/finecflowsmatrixbootstrap.Rdata"))
write.csv(bsfinecflows, file = "./finalresults/finecflowsmatrixbootstrap.csv", row.names = FALSE)

save(bsfinefish     , file = paste0("./finalresults/finefishmatrixbootstrap.Rdata"))
write.csv(bsfinefish, file = "./finalresults/finefishmatrixbootstrap.csv", row.names = FALSE)

```

# Indices


-   Calculated on average of MCMC solution and on initial solution
    (Ldei).

## Calculate on output rows

```{r, options}

# Create Index matrix #
Indices     <- c("T..", "TST", "Ltot", "Lint", "LD",
             "C", "Tij", "FCI", "APL", "HR", "DR", "AMI", "ACR", "BC", "Cbar", "TSTC", "TSTS")
readLIM     <- readLIM.fine
variranges  <- varrangesfine
finalmatrix <- XFine
LIM         <- LIM.fine

seq <- round(seq(1, nrow(XFine), length.out = 1000), 0)

# Create a matrix for the indices to be calculated for each iteration
NetInd <- matrix(NA, nrow = length(seq), ncol = length(Indices)) ##dimnames
colnames(NetInd) <- Indices

# Matrix for trophic level calculation
comps <- as.character(LIM$Components$name)
TrLevels <- matrix(NA, nrow = length(seq), ncol = length(comps))
colnames(TrLevels) <- comps

TrOI <- matrix(NA, nrow = length(seq), ncol = length(comps))
colnames(TrOI) <- comps

# Loop
for (i in 1:length(seq)){
  
  # Specify which compartments are external to serve for import and export.
  # Specify which compartments comprise of dead material.
  Import <- c("DIC")
  Export <- c("EXP", "DIC", "BUR")
  Dead   <- c("SOM", "SPOM")
  
  # Get flow matrix 
  fm  <- getFlowMatrix(originalFM = LIM$Flowmatrix, 
                       flows = readLIM$flows, 
                       answers = finalmatrix[i,])
  
  # Remove rows/cols that sum to zero,
  # and remove Imports from colums and Exports from rows.
  RemCol <- unique(which(colSums(fm)==0), 
                   which(colnames(fm)%in% Import, arr.ind = TRUE))
  RemRow <- unique(which(rowSums(fm)==0), 
                   which(rownames(fm)%in% Export, arr.ind = TRUE))
  if(length(RemRow) != 0) {fm <- fm[-RemRow,] }
  if(length(RemCol) != 0) {fm <- fm[,-RemCol] }
  
  # Redefine Import and Export if they were eliminated from fm
  Import <- Import[which(Import%in%rownames(fm))]      
  Export <- Export[which(Export%in%colnames(fm))]      

  # Calculate indices
  NetInd[i, "T.."]  <- GenInd (Flow=fm, Import=Import, Export=Export)$T..
  NetInd[i, "TST"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$TST
  NetInd[i, "Lint"] <- GenInd (Flow=fm, Import=Import, Export=Export)$Lint
  NetInd[i, "Ltot"] <- GenInd (Flow=fm, Import=Import, Export=Export)$Ltot
  NetInd[i, "LD"]   <- GenInd (Flow=fm, Import=Import, Export=Export)$LD
  NetInd[i, "C"]    <- GenInd (Flow=fm, Import=Import, Export=Export)$C
  NetInd[i, "Tij"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$Tij
  NetInd[i, "FCI"]  <- PathInd(Flow=fm, Import=Import, Export=Export)$FCIb
  NetInd[i, "APL"]  <- PathInd(Flow=fm, Import=Import, Export=Export)$APL
  NetInd[i, "HR"]   <- UncInd (Flow=fm, Import=Import, Export=Export)$HR
  NetInd[i, "DR"]   <- UncInd (Flow=fm, Import=Import, Export=Export)$DR
  NetInd[i, "AMI"]  <- UncInd (Flow=fm, Import=Import, Export=Export)$AMI
  NetInd[i, "ACR"]  <- AscInd (Flow=fm, Import=Import, Export=Export) ["Total","ACratio"]
  NetInd[i, "BC"]   <- EnvInd (Flow=fm, Import=Import, Export=Export)$BC
  NetInd[i, "Cbar"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$Cbar
  NetInd[i, "TSTC"]  <- PathInd (Flow=fm, Import=Import, Export=Export)$TSTC
  NetInd[i, "TSTS"]  <- PathInd (Flow=fm, Import=Import, Export=Export)$TSTS

  a <- getTrophInd(Flow=fm, Import=Import, Export=Export, Dead=Dead)$TL
  if(length(a) != length(comps)) {
    index <- index[!is.na(index)]
    for (j in 1:length(index)) {
      val <- c(a, NA)
      id  <- c(seq_along(a), index[j]-0.5)
      a <- val[order(id)]
    }
  }
  TrLevels[i,] <- a
  
  b <- getTrophInd(Flow=fm, Import=Import, Export=Export, Dead=Dead)$OI
  if(length(b) != length(comps)) {
    index <- index[!is.na(index)]
    for (j in 1:length(index)) {
      val <- c(b, NA)
      id  <- c(seq_along(b), index[j]-0.5)
      b <- val[order(id)]
    }
  }
  TrOI[i,] <- b
  
} 

netindfine <- NetInd

rm(NetInd)

save(file = "./finalresults/NETINDfine.rda", netindfine)


```

## Analysis of index results

```{r}

load(file = "./finalresults/NETINDfine.rda")

# Save mean±std for use in text.
meansNI <- colMeans(netindfine)
stdevNI <- sqrt(diag(var(netindfine)))
NIfine  <- data.frame(mean = meansNI, stdev = stdevNI)

save(file = "./finalresults/fineindtable.rda", NIfine)

```

# Calculate variables

```{r}


varA <- NULL

for(i in (1:nrow(XFine))){
varnew <- LIM.fine$VarA%*%XFine[i,]
varA <- cbind(varA, varnew)
}

varsfine <- varA
rm(varA)

row.names(varsfine) <- LIM.fine$Variables

meanvarsfine <- apply(varsfine, 1, mean, na.rm = TRUE)
sdvarsfine   <- apply(varsfine, 1, sd, na.rm = TRUE)
minvarsfine  <- apply(varsfine, 1, min, na.rm = TRUE)
maxvarsfine  <- apply(varsfine, 1, max, na.rm = TRUE)

varsfine <- data.frame("mean" = meanvarsfine, "sd" = sdvarsfine, "min" = minvarsfine, "max" = maxvarsfine)

save(file = "./finalresults/varsfine.rda", varsfine)
write.csv(varsfine, file = "./finalresults/varsfine.csv") 

```
