---
title: "Coarse foodweb model"
author: "Emil De Borger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  markdown: 
    wrap: 72
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---

# Description

-   Runs the foodweb as specified in `/final_versions/coarse.input`.

-   Links between groups based on literature research.

-   Ldei: Solves a linear inverse model using least distance programming
    (i.e. minimizes sum of squared unknowns). $\min(∑ {Cost_i*x_i}^2)$
    Subject to equalities and inequalities: $Ax = B$ $Gx>=H$

-   ldei: Solves *underdetermined* inverse problem $\min(∑ {x_i}^2)$
    subject to equalities and inequalities: $Ax = B$ $Gx>=H$
    Underdetermined: number of independent equations \< number of
    unknowns.

```{r setup, include=FALSE}

# Packages 
require(LIM)
require(splus2R)
require(NetIndices)
require(MASS)
require(xlsx)
require(vegan)

# Files
File.coarse <- "./final_versions/coarse.input"

```

# Reading LIM and run ranges

### Read LIM

```{r}

readLIM.coarse  <- LIM::Read(file = File.coarse, verbose = TRUE, checkLinear = TRUE)

```

# Solving LIM

### Single solution and ranges

```{r}

# Ranges and solution
readLIM.coarse  <- LIM::Read(file=File.coarse, verbose = TRUE, checkLinear = TRUE)
LIM.coarse      <- Setup(readLIM.coarse)
Solldeicoarse   <- Ldei(LIM.coarse, verbose = T)
Rangescoarse    <- Xranges(LIM.coarse, central = T, ispos = T)
varrangescoarse <- Varranges(LIM.coarse)

# Check validity of solution (multiply vector solution w eq matrix)
any((LIM.coarse$A %*% Solldeicoarse$X - LIM.coarse$B)>1e-8)
any((LIM.coarse$G %*% Solldeicoarse$X - LIM.coarse$H)<(-1E-8))

save(readLIM.coarse , file = "./finalresults/readlimcoarse.rda")
save(LIM.coarse     , file = "./finalresults/limcoarse.rda")
save(Solldeicoarse  , file = "./finalresults/solldeicoarse.rda")
save(Rangescoarse   , file = "./finalresults/rangescoarse.rda")
save(varrangescoarse, file = "./finalresults/varrangescoarse.rda")

```

### Cluster computing

- Evaluated online on NIOZ BIOINFORMATICS server

### Load .rda elements

```{r label, options}

load(file = "./330_export/MCMCcoarse.rda")
XCoarse <- mcExtract(mcmccoarse)

```

# Analysis of fluxes

### Calculate mean-sd of flows

```{r}

finalmatrix <- XCoarse
LIM         <- LIM.coarse
readLIM     <- readLIM.coarse
variranges  <- varrangescoarse

prodcoarsesel <- c(4, 8, 12, 16, 20, 24, 28, 32, 36, 40)

# Mean + SD of solutions.
### Get mean±std
meanvalues  <- cbind(LIM$Unknowns, colMeans(finalmatrix))
standarddev <- cbind(LIM$Unknowns, sqrt(diag(var(finalmatrix))))

### Add to dataframe
minimum <- apply(finalmatrix, 2, min, na.rm = TRUE)
maximum <- apply(finalmatrix, 2, max, na.rm = TRUE)

flow         <- meanvalues[,1]
mean         <- as.numeric(meanvalues[,2])
std          <- as.numeric(standarddev[,2])
Flows.Coarse <- data.frame(flow, mean, std, minimum, maximum)

### Save as excel sheet.
write.csv(Flows.Coarse, paste("./finalresults/Flows_coarse_iso.csv"))

### The Flows data frame is saved as .Rdata file
save(Flows.Coarse, file = paste0("./finalresults/Flows_coarse_iso.Rdata"))

### Get Flowmatrix with Bayesian solution.
FM.Coarse <- getFlowMatrix(originalFM = LIM$Flowmatrix, 
                        flows      = readLIM$flows , 
                        answers    = Flows.Coarse[,"mean"])

# Mean + SD of variable estimates
Vals      <- data.frame(variranges)
Vals$mean <- numeric(LIM$NVariables)
Vals$std  <- numeric(LIM$NVariables)
  
vareq      <- readLIM$vars # matrix which defines the variable equations
parvec     <- readLIM$pars$val # vector with parameter values
flowvec    <- as.numeric(meanvalues[,2]) # vector with mean flow values
flowstdvec <- as.numeric(standarddev[,2]) # vector with flow standard deviations

for (j in 1:LIM$NVariables) {
  # refresh vector with mean and std values
  varvec <- Vals$mean
  varstdvec <- Vals$std
  
  # Get subset with the same equation nr.
  subset <- vareq[vareq$nr == j,] 
    
  # Take parameter, variable or flow nr from subset to use as index. 
  # Use index to find the corresponding values.
  # Multiply the values by 'val' which is the coefficient (like 1 or -1) and sum them.
  sum <- 
    sum(parvec[subset$par1]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par2]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par3]*subset$val, na.rm = TRUE) +
    sum(parvec[subset$par4]*subset$val, na.rm = TRUE) +
    sum(varvec[subset$var]*subset$val, na.rm = TRUE) +
    sum(flowvec[subset$flow]*subset$val, na.rm = TRUE)  
  
  # Use index to find corresponding standard deviations.
  # Sum squared standard deviations and take the square root.
  stddev <- 
    sqrt(
      sum(flowstdvec[subset$flow]^2, na.rm = TRUE) +
        sum(varstdvec[subset$var]^2, na.rm = TRUE)
    )
  
  # Add values to data frame.
  Vals$mean[j] = sum 
  Vals$std[j]  = stddev
}
  
# The Vals data frame is saved as .Rdata file.
Vals_Coarse <- Vals
save(Vals_Coarse, file = paste0("./finalresults/vals_Coarse_iso.Rdata"))

# Clean up memory
rm(finalmatrix, readLIM, LIM,
   meanvalues, mean,
   standarddev, std, stddev, 
   flow, maximum, minimum, sum,
   parvec, varstdvec, flowstdvec, vareq, flowvec,
   Vals, variranges, subset)

```

### Summary of fluxes

```{r}

Fish     <- c(LIM.coarse$Components$name[1:10]) #String with fish.
Benthos  <- c(LIM.coarse$Components$name[12:35]) #String with benthos.

bivalves    <- c(LIM.coarse$Components$name[30:32])  
crustacea   <- c(LIM.coarse$Components$name[12:20]) 
polychaetes <- c(LIM.coarse$Components$name[24:29]) 
others      <- c(LIM.coarse$Components$name[c(21:23, 33:35)]) 

phytobenth <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", Benthos)))
zoobenth   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", Benthos)))
spombenth  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", Benthos)))
sombenth   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", Benthos)))
benthbenth <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, Benthos, sep="->"))))

phytobiv <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", bivalves)))
zoobiv   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", bivalves)))
spombiv  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", bivalves)))
sombiv   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", bivalves)))
benthbiv <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, bivalves, sep="->"))))

phytocrust <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", crustacea)))
zoocrust   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", crustacea)))
spomcrust  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", crustacea)))
somcrust   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", crustacea)))
benthcrust <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, crustacea, sep="->"))))

phytopoly <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", polychaetes)))
zoopoly   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", polychaetes)))
spompoly  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", polychaetes)))
sompoly   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", polychaetes)))
benthpoly <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, polychaetes, sep="->"))))

phytooth <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", others)))
zoooth   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", others)))
spomoth  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", others)))
somoth   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", others)))
benthoth <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, others, sep="->"))))

cflows    <- c("OM deposition"         ,
               "Fish respiration"      ,
               "Jellyfish respiration" , 
               "Bacterial respiration" ,
               "Macrofauna respiration",
               "Sediment respiration"  ,
               "Water respiration"     ,
               "Total respiration"     ,
               "Burial"                ,
               "Total export"          ,
               "phytoplankton uptake macrofauna",
               "zooplankton uptake macrofauna"  ,
               "SOM uptake macrofauna"          ,
               "SPOM uptake macrofauna"         ,
               "Total uptake macrofauna"        ,
               "SOM uptake bacteria"            ,
               "SPOM uptake bacteria"           , 
               "Uptake water bivalves"          ,
               "Uptake water crustaceans"       ,
               "Uptake water polychaetes"       ,
               "Uptake water others"            ,
               "Uptake SOM bivalves"            ,
               "Uptake SOM crustaceans"         ,
               "Uptake SOM polychaetes"         ,
               "Uptake SOM others"              ,
               "Total carbon outflow"           ,
               "Total carbon inflow"            ,
               "Phyto->Zoo",
               "Zoo->SPOM",
               "Phyto->SPOM",
               "Zoo->Fish",
               "SPOM->Fish",
               "Fish->SPOM",
               "WatBac->DIC",
               "SPOM->WatBac",
               "WatBac->SPOM",
               "Zoo->Jelly",
               "Jelly->SPOM",
               "SOM->SedBac",
               "SedBac->SOM",
               "SOM->Burial",
               "SedBac->Burial",
               "Benthos->Fish",
               "Zoo->DIC",
               "Fish->DIC",
               "Jelly->DIC",
               "SedBac->DIC",
               "Benthos->DIC",
               "DIC->Phyto",
               "Benthos->SOM",
               "Phyto->Benthos",
               "Zoo->Benthos",
               "SPOM->Benthos",
               "SOM->Benthos",
               "Benthos->Benthos",
               "Phyto->Bivalves",
               "Zoo->Bivalves",
               "SPOM->Bivalves",
               "SOM->Bivalves",
               "Benthos->Bivalves",
               "Phyto->Crustaceans",
               "Zoo->Crustaceans",
               "SPOM->Crustaceans",
               "SOM->Crustaceans",
               "Benthos->Crustaceans",
               "Phyto->Polychaetes",
               "Zoo->Polychaetes",
               "SPOM->Polychaetes",
               "SOM->Polychaetes",
               "Benthos->Polychaetes",
               "Phyto->Others",
               "Zoo->Others",
               "SPOM->Others",
               "SOM->Others",
               "Benthos->Others",
               "Phyto->Export",
               "Zoo->Export",
               "Fish->Export",
               "Jelly->Export",
               "Benthos->Export")

restabcoarse <- data.frame(name = cflows, mean = NA, std = NA, min = NA, max = NA)

ii <- list(grep("SPOM->SOM", Flows.Coarse$flow), # OM deposition
           c(376:385) ,                       # Fish respiration
           c(386)     ,                       # Jellyfish respiration
           c(411:412) ,                       # Bacterial respiration
           c(387:409) ,                       # Macrofauna respiration
           c(387:410) ,                       # SCOC
           c(376:386, 413),                   # Water respiration - phytoplankton
           c(376:413)     ,                   # Total respiration - phytoplankton
           c(453)         ,                   # Burial
           c(414:452)     ,                   # Total export
           grep("PHYTOPLANKT->", Flows.Coarse$flow)[-c(8:10)]  , # Phyto uptake macrofauna 
           grep("ZOOPLANKT->"  , Flows.Coarse$flow)[c(12:19)]  , # Zoo uptake macrofauna
           grep("SOM->"        , Flows.Coarse$flow)[c(5:22)]   , # SOM uptake macrofauna
           grep("SPOM->"       , Flows.Coarse$flow)[c(3:13)]   , # SPOM uptake macrofauna
           c(grep("PHYTOPLANKT->", Flows.Coarse$flow)[-c(8:10)], # Total uptake macrofauna
           grep("ZOOPLANKT->"  , Flows.Coarse$flow)[c(12:19)]  ,
           grep("SOM->"        , Flows.Coarse$flow)[c(5:22)]   ,
           grep("SPOM->"       , Flows.Coarse$flow)[c(3:13)])  ,
           grep("SOM->SEDBAC" , Flows.Coarse$flow)             , # SOM uptake bacteria
           grep("SPOM->WATBAC", Flows.Coarse$flow)             , # SPOM uptake bacteria
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Coarse$flow)[c(30:37)]     , # Uptake water bivalves
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Coarse$flow)[c(14:25)]      , # Uptake water crustaceans
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Coarse$flow)[c(27:29)]     , # Uptake water polychaetes
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", Flows.Coarse$flow)[c(26, 38:40)], # Uptake water others
           grep("SOM->", Flows.Coarse$flow)[c(20, 21)]   , # Uptake SOM bivalves
           grep("SOM->", Flows.Coarse$flow)[c(3:11)]     , # Uptake SOM crustaceans
           grep("SOM->", Flows.Coarse$flow)[c(15:19)]    , # Uptake SOM polychaetes
           grep("SOM->", Flows.Coarse$flow)[c(12:14, 22)], # Uptake SOM others
           c(c(376:453)),                               # Total C outflow
           grep("DIC->PHYTOPLANKT", Flows.Coarse$flow),    # Total C inflow
           grep("PHYTOPLANKT->ZOOPLANKT", Flows.Coarse$flow),
           grep("ZOOPLANKT->SPOM", Flows.Coarse$flow),
           grep("PHYTOPLANKT->SPOM", Flows.Coarse$flow),
           grep("ZOOPLANKT->", Flows.Coarse$flow)[c(1:10)],
           grep("SPOM->", Flows.Coarse$flow)[c(1)],
           grep("->SPOM", Flows.Coarse$flow)[c(2:11)], 
           grep("WATBAC->DIC", Flows.Coarse$flow),
           grep("SPOM->WATBAC", Flows.Coarse$flow),
           grep("WATBAC->SPOM", Flows.Coarse$flow),
           grep("ZOOPLANKT->JELLY", Flows.Coarse$flow),
           grep("JELLY->SPOM", Flows.Coarse$flow),
           grep("SOM->SEDBAC", Flows.Coarse$flow),
           grep("SEDBAC->SOM", Flows.Coarse$flow),
           grep("SOM->BUR", Flows.Coarse$flow),
           grep("SEDBAC->BUR", Flows.Coarse$flow),
           c(1:19,22:28, 38:55, 58:74, 76, 80:97, 100:116, 119:132, 140:147, 153:157, 161:181, 184:186),
           grep("ZOOPLANKT->DIC", Flows.Coarse$flow),
           grep("->DIC", Flows.Coarse$flow)[1:10],
           grep("->DIC", Flows.Coarse$flow)[11],
           grep("SEDBAC->DIC", Flows.Coarse$flow),
           grep("->DIC", Flows.Coarse$flow)[12:35],
           grep("DIC->PHYTOPLANKT", Flows.Coarse$flow),
           grep("->SOM", Flows.Coarse$flow)[3:26],
           phytobenth                         ,
           zoobenth                           ,
           spombenth                          ,
           sombenth                           ,
           benthbenth                         ,
           phytobiv                           ,
           zoobiv                             ,
           spombiv                            ,
           sombiv                             ,
           benthbiv                           ,
           phytocrust                         ,
           zoocrust                           ,
           spomcrust                          ,
           somcrust                           ,
           benthcrust                         ,
           phytopoly                          ,
           zoopoly                            ,
           spompoly                           ,
           sompoly                            ,
           benthpoly                          ,
           phytooth                           ,
           zoooth                             ,
           spomoth                            ,
           somoth                             ,
           benthoth                           ,
           c(450)                             ,
           c(449)                             ,
           c(414:423)                         ,
           c(424)                             ,
           c(426:448)
)

        

for(i in 1:length(ii)){
  restabcoarse[i,"mean"] <- sum(Flows.Coarse$mean[ii[[i]]])
  restabcoarse[i,"std"]  <- stdfromstd(Flows.Coarse$std[ii[[i]]])
  restabcoarse[i,"min"]  <- sum(Flows.Coarse$minimum[ii[[i]]])
  restabcoarse[i,"max"]  <- sum(Flows.Coarse$maximum[ii[[i]]])
}

knitr::kable(restabcoarse)

save(restabcoarse, file = paste0("./finalresults/restab_coarse_iso.Rdata"))

write.csv(restabcoarse, file = "./finalresults/restabcoarse.csv", row.names = FALSE)


#### Fish

Fishcoarse <- NULL

for(i in Fish){
  
  ii <- list(
  phy   <- which(Flows.Coarse$flow %in% c(paste0("PHYTOPLANKT->", i))),
  zoo   <- which(Flows.Coarse$flow %in% c(paste0("ZOOPLANKT->", i))),
  spom  <- which(Flows.Coarse$flow %in% c(paste0("SPOM->", i))),
  som   <- which(Flows.Coarse$flow %in% c(paste0("SOM->", i))),
  benth <- which(Flows.Coarse$flow %in% c(levels(interaction(Benthos, i, sep="->")))),
  biv   <- which(Flows.Coarse$flow %in% c(levels(interaction(bivalves, i, sep="->")))),
  cru   <- which(Flows.Coarse$flow %in% c(levels(interaction(crustacea, i, sep="->")))),
  pol   <- which(Flows.Coarse$flow %in% c(levels(interaction(polychaetes, i, sep="->")))),
  oth   <- which(Flows.Coarse$flow %in% c(levels(interaction(others, i, sep="->")))), 
  pisc  <- which(Flows.Coarse$flow %in% c(levels(interaction(Fish, i, sep="->"))))
  )
  
  nms <- c("Phyto", "Zoo", "SPOM", "SOM", "Benthos", "Biv", "Crust", "Poly", "Other", "Pisc")
  new <- data.frame(name = nms, mean = NA, std = NA, min = NA, max = NA)

  for(j in 1:length(ii)){
  new[j, "Fish"] <- i
  new[j,"mean"] <- sum(Flows.Coarse$mean[ii[[j]]])
  new[j,"std"]  <- stdfromstd(Flows.Coarse$std[ii[[j]]])
  new[j,"min"]  <- sum(Flows.Coarse$minimum[ii[[j]]])
  new[j,"max"]  <- sum(Flows.Coarse$maximum[ii[[j]]])
  }
  
  Fishcoarse <- rbind(Fishcoarse, new)
  
}

save(Fishcoarse     , file = paste0("./finalresults/fish_coarse_iso.Rdata"))
write.csv(Fishcoarse, file = "./finalresults/fishcoarse.csv", row.names = FALSE)

```

# Matrix for bootstrapping comparison

```{r}

bscoarse <- XCoarse
colnames(bscoarse) <- Flows.Coarse$flow

ii <- list(grep("SPOM->SOM", colnames(bscoarse)), # OM deposition
           c(376:385) ,                       # Fish respiration
           c(386)     ,                       # Jellyfish respiration
           c(411:412) ,                       # Bacterial respiration
           c(387:409) ,                       # Macrofauna respiration
           c(387:410) ,                       # SCOC
           c(376:386, 413),                   # Water respiration - phytoplankton
           c(376:413)     ,                   # Total respiration - phytoplankton
           c(453)         ,                   # Burial
           c(414:452)     ,                   # Total export
           grep("PHYTOPLANKT->", colnames(bscoarse))[-c(8:10)]  , # Phyto uptake macrofauna 
           grep("ZOOPLANKT->"  , colnames(bscoarse))[c(12:19)]  , # Zoo uptake macrofauna
           grep("SOM->"        , colnames(bscoarse))[c(5:22)]   , # SOM uptake macrofauna
           grep("SPOM->"       , colnames(bscoarse))[c(3:13)]   , # SPOM uptake macrofauna
           c(grep("PHYTOPLANKT->", colnames(bscoarse))[-c(8:10)], # Total uptake macrofauna
           grep("ZOOPLANKT->"  , colnames(bscoarse))[c(12:19)]  ,
           grep("SOM->"        , colnames(bscoarse))[c(5:22)]   ,
           grep("SPOM->"       , colnames(bscoarse))[c(3:13)])  ,
           grep("SOM->SEDBAC" , colnames(bscoarse))             , # SOM uptake bacteria
           grep("SPOM->WATBAC", colnames(bscoarse))             , # SPOM uptake bacteria
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bscoarse))[c(30:37)]     , # Uptake water bivalves
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bscoarse))[c(14:25)]      , # Uptake water crustaceans
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bscoarse))[c(27:29)]     , # Uptake water polychaetes
           grep("PHYTOPLANKT->|ZOOPLANKT->|SPOM->", colnames(bscoarse))[c(26, 38:40)], # Uptake water others
           grep("SOM->", colnames(bscoarse))[c(20, 21)]   , # Uptake SOM bivalves
           grep("SOM->", colnames(bscoarse))[c(3:11)]     , # Uptake SOM crustaceans
           grep("SOM->", colnames(bscoarse))[c(15:19)]    , # Uptake SOM polychaetes
           grep("SOM->", colnames(bscoarse))[c(12:14, 22)], # Uptake SOM others
           c(c(376:453)),                               # Total C outflow
           grep("DIC->PHYTOPLANKT", colnames(bscoarse)),    # Total C inflow
           grep("PHYTOPLANKT->ZOOPLANKT", colnames(bscoarse)),
           grep("ZOOPLANKT->SPOM", colnames(bscoarse)),
           grep("PHYTOPLANKT->SPOM", colnames(bscoarse)),
           grep("ZOOPLANKT->", colnames(bscoarse))[c(1:10)],
           grep("SPOM->", colnames(bscoarse))[c(1)],
           grep("->SPOM", colnames(bscoarse))[c(2:11)], 
           grep("WATBAC->DIC", colnames(bscoarse)),
           grep("SPOM->WATBAC", colnames(bscoarse)),
           grep("WATBAC->SPOM", colnames(bscoarse)),
           grep("ZOOPLANKT->JELLY", colnames(bscoarse)),
           grep("JELLY->SPOM", colnames(bscoarse)),
           grep("SOM->SEDBAC", colnames(bscoarse)),
           grep("SEDBAC->SOM", colnames(bscoarse)),
           grep("SOM->BUR", colnames(bscoarse)),
           grep("SEDBAC->BUR", colnames(bscoarse)),
           c(1:19,22:28, 38:55, 58:74, 76, 80:97, 100:116, 119:132, 140:147, 153:157, 161:181, 184:186),
           grep("ZOOPLANKT->DIC", colnames(bscoarse)),
           grep("->DIC", colnames(bscoarse))[1:10],
           grep("->DIC", colnames(bscoarse))[11],
           grep("SEDBAC->DIC", colnames(bscoarse)),
           grep("->DIC", colnames(bscoarse))[12:35],
           grep("DIC->PHYTOPLANKT", colnames(bscoarse)),
           grep("->SOM", colnames(bscoarse))[3:26],
           phytobenth                         ,
           zoobenth                           ,
           spombenth                          ,
           sombenth                           ,
           benthbenth                         ,
           phytobiv                           ,
           zoobiv                             ,
           spombiv                            ,
           sombiv                             ,
           benthbiv                           ,
           phytocrust                         ,
           zoocrust                           ,
           spomcrust                          ,
           somcrust                           ,
           benthcrust                         ,
           phytopoly                          ,
           zoopoly                            ,
           spompoly                           ,
           sompoly                            ,
           benthpoly                          ,
           phytooth                           ,
           zoooth                             ,
           spomoth                            ,
           somoth                             ,
           benthoth                           ,
           c(450)                             ,
           c(449)                             ,
           c(414:423)                         ,
           c(424)                             ,
           c(426:448)
)

bscoarsecflows <- data.frame(matrix(data = NA, nrow = 9950))

for(i in 1:length(ii)){
  bscoarsecflows <- cbind(bscoarsecflows, rowSums(cbind(bscoarse[,ii[[i]]], rep(0, 9950))))
}

bscoarsecflows <- bscoarsecflows[,-1]
colnames(bscoarsecflows) <- cflows

#################################


bscoarsefish <- data.frame(matrix(data = NA, nrow = 9950))
namevec <- NULL

i <- Fish[1]

for(i in Fish){
  
  ii <- list(
  phy   <- which(colnames(bscoarse) %in% c(paste0("PHYTOPLANKT->", i))),
  zoo   <- which(colnames(bscoarse) %in% c(paste0("ZOOPLANKT->", i))),
  spom  <- which(colnames(bscoarse) %in% c(paste0("SPOM->", i))),
  som   <- which(colnames(bscoarse) %in% c(paste0("SOM->", i))),
  benth <- which(colnames(bscoarse) %in% c(levels(interaction(Benthos, i, sep="->")))),
  biv   <- which(colnames(bscoarse) %in% c(levels(interaction(bivalves, i, sep="->")))),
  cru   <- which(colnames(bscoarse) %in% c(levels(interaction(crustacea, i, sep="->")))),
  pol   <- which(colnames(bscoarse) %in% c(levels(interaction(polychaetes, i, sep="->")))),
  oth   <- which(colnames(bscoarse) %in% c(levels(interaction(others, i, sep="->")))), 
  pisc  <- which(colnames(bscoarse) %in% c(levels(interaction(Fish, i, sep="->"))))
  )
  
  nms <- paste0(i, "_", c("Phyto", "Zoo", "SPOM", "SOM", "Benthos", "Biv", "Crust", "Poly", "Other", "Pisc"))

  for(j in 1:length(ii)){
    bscoarsefish <- cbind(bscoarsefish, rowSums(bscoarse[,ii[[j]], drop = FALSE]))
  }
  
  namevec <- c(namevec, nms)
  
}

bscoarsefish <- bscoarsefish[,-1]
colnames(bscoarsefish) <- namevec


save(bscoarsecflows     , file = paste0("./finalresults/coarsecflowsmatrixbootstrap.Rdata"))
write.csv(bscoarsecflows, file = "./finalresults/coarsecflowsmatrixbootstrap.csv", row.names = FALSE)

save(bscoarsefish     , file = paste0("./finalresults/coarsefishmatrixbootstrap.Rdata"))
write.csv(bscoarsefish, file = "./finalresults/coarsefishmatrixbootstrap.csv", row.names = FALSE)

```

# Indices

-   Calculated on average of MCMC solution and on initial solution
    (Ldei).

## Calculate on output rows

```{r, options}

# Create Index matrix #
Indices     <- c("T..", "TST", "Ltot", "Lint", "LD",
             "C", "Tij", "FCI", "APL", "HR", "DR", "AMI", "ACR", "BC", "Cbar", "TSTC", "TSTS")
readLIM     <- readLIM.coarse
variranges  <- varrangescoarse
finalmatrix <- XCoarse
LIM         <- LIM.coarse

seq <- round(seq(1, nrow(XCoarse), length.out = 1000), 0)

# Create a matrix for the indices to be calculated for subset of iterations
NetInd <- matrix(NA, nrow = length(seq), ncol = length(Indices)) ##dimnames
colnames(NetInd) <- Indices

# Matrix for trophic level calculation and omnivory index
comps <- as.character(LIM$Components$name)

TrLevels <- matrix(NA, nrow = length(seq), ncol = length(comps))
colnames(TrLevels) <- comps

TrOI     <- matrix(NA, nrow = length(seq), ncol = length(comps))
colnames(TrOI) <- comps

# Loop
for (i in 1:length(seq)){
  
  # Specify which compartments are external to serve for import and export.
  # Specify which compartments comprise of dead material.
  Import <- c("DIC")
  Export <- c("EXP", "DIC", "BUR")
  Dead   <- c("SOM", "SPOM")
  
  # Get flow matrix 
  fm  <- getFlowMatrix(originalFM = LIM$Flowmatrix, 
                       flows = readLIM$flows, 
                       answers = finalmatrix[i,])
  
  # Remove rows/cols that sum to zero,
  # and remove Imports from colums and Exports from rows.
  RemCol <- unique(which(colSums(fm)==0), 
                   which(colnames(fm)%in% Import, arr.ind = TRUE))
  RemRow <- unique(which(rowSums(fm)==0), 
                   which(rownames(fm)%in% Export, arr.ind = TRUE))
  if(length(RemRow) != 0) {fm <- fm[-RemRow,] }
  if(length(RemCol) != 0) {fm <- fm[,-RemCol] }
  
  # Redefine Import and Export if they were eliminated from fm
  Import <- Import[which(Import%in%rownames(fm))]      
  Export <- Export[which(Export%in%colnames(fm))]      

  # Calculate indices
  NetInd[i, "T.."]  <- GenInd (Flow=fm, Import=Import, Export=Export)$T..
  NetInd[i, "TST"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$TST
  NetInd[i, "Lint"] <- GenInd (Flow=fm, Import=Import, Export=Export)$Lint
  NetInd[i, "Ltot"] <- GenInd (Flow=fm, Import=Import, Export=Export)$Ltot
  NetInd[i, "LD"]   <- GenInd (Flow=fm, Import=Import, Export=Export)$LD
  NetInd[i, "C"]    <- GenInd (Flow=fm, Import=Import, Export=Export)$C
  NetInd[i, "Tij"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$Tij
  NetInd[i, "FCI"]  <- PathInd(Flow=fm, Import=Import, Export=Export)$FCIb
  NetInd[i, "APL"]  <- PathInd(Flow=fm, Import=Import, Export=Export)$APL
  NetInd[i, "HR"]   <- UncInd (Flow=fm, Import=Import, Export=Export)$HR
  NetInd[i, "DR"]   <- UncInd (Flow=fm, Import=Import, Export=Export)$DR
  NetInd[i, "AMI"]  <- UncInd (Flow=fm, Import=Import, Export=Export)$AMI
  NetInd[i, "ACR"]  <- AscInd (Flow=fm, Import=Import, Export=Export) ["Total","ACratio"]
  NetInd[i, "BC"]   <- EnvInd (Flow=fm, Import=Import, Export=Export)$BC
  NetInd[i, "Cbar"]  <- GenInd (Flow=fm, Import=Import, Export=Export)$Cbar
  NetInd[i, "TSTC"]  <- PathInd (Flow=fm, Import=Import, Export=Export)$TSTC
  NetInd[i, "TSTS"]  <- PathInd (Flow=fm, Import=Import, Export=Export)$TSTS
  
  a <- getTrophInd(Flow=fm, Import=Import, Export=Export, Dead=Dead)$TL
  if(length(a) != length(comps)) {
    index <- index[!is.na(index)]
    for (j in 1:length(index)) {
      val <- c(a, NA)
      id  <- c(seq_along(a), index[j]-0.5)
      a <- val[order(id)]
    }
  }
  TrLevels[i,] <- a
  
  b <- getTrophInd(Flow=fm, Import=Import, Export=Export, Dead=Dead)$OI
  if(length(b) != length(comps)) {
    index <- index[!is.na(index)]
    for (j in 1:length(index)) {
      val <- c(b, NA)
      id  <- c(seq_along(b), index[j]-0.5)
      b <- val[order(id)]
    }
  }
  TrOI[i,] <- b
  
} 

netindcoarse <- NetInd

rm(NetInd)

save(file = "./finalresults/NETINDCOARSE.rda", netindcoarse)


```

## Analysis of index results

```{r}

load(file = "./finalresults/NETINDCOARSE.rda")

# Save mean±std for use in text.
meansNI <- colMeans(netindcoarse)
stdevNI <- sqrt(diag(var(netindcoarse)))
NICOARSE   <- data.frame(mean = meansNI, stdev = stdevNI)

save(file = "./finalresults/coarseindtable.rda", NICOARSE)

```

# Calculate variables

```{r}

varA <- NULL

for(i in (1:nrow(XCoarse))){
varnew <- LIM.coarse$VarA%*%XCoarse[i,]
varA <- cbind(varA, varnew)
}

varscoarse <- varA
rm(varA)

row.names(varscoarse) <- LIM.coarse$Variables

meanvarscoarse <- apply(varscoarse, 1, mean, na.rm = TRUE)
sdvarscoarse   <- apply(varscoarse, 1, sd, na.rm = TRUE)
minvarscoarse  <- apply(varscoarse, 1, min, na.rm = TRUE)
maxvarscoarse  <- apply(varscoarse, 1, max, na.rm = TRUE)

varscoarse <- data.frame("mean" = meanvarscoarse, "sd" = sdvarscoarse, "min" = minvarscoarse, "max" = maxvarscoarse)

save(file = "./finalresults/varscoarse.rda", varscoarse)
write.csv(varscoarse, file = "./finalresults/varscoarse.csv") 

```